### 2019-04-19 Report/paper.tex
Added Paper Skeleton

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\documentclass[runningheads,a4paper]{llncs}
\documentclass[runningheads]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{amsmath}
\usepackage{listings}

\usepackage{verbatim}
\usepackage{longtable}
\usepackage[table]{xcolor}
\usepackage{tabularx, booktabs}
\usepackage{multirow}
\usepackage{epsfig}
\usepackage{pdflscape}

%\usepackage{algorithm2e}
%\usepackage[linesnumbered]{algorithm2e}
%\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}

\newcolumntype{Y}{>{\centering\arraybackslash}X}

% \renewcommand{\ttdefault}{pcr} % makes bold available in a fixed-width font (use )

\lstMakeShortInline[basicstyle=\small]|

\lstset{
%    numbers=left
  , numberstyle=\tiny, stepnumber=5, firstnumber=1, numbersep=5pt
  , language=[Sharp]C
  , breaklines=true
  , tabsize=4
  , columns=fullflexible
  , keepspaces=true
  , basicstyle=\fontfamily{lmtt}\selectfont  % fixed-width font (better, but too wide for 2-column layout)
  , captionpos=t
  , frame=single
}

%%\usepackage{url}
%%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
%%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
%%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
%%\newcommand{\keywords}[1]{\par\addvspace\baselineskip
%%\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{An Algorithm for In-Situ Bus Scheduling and Passenger State Update}

% a short form should be given in case it is too long for the running head
\titlerunning{In-Situ Bus Scheduling}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Yung-Fu Chen \and Alan Weide}
\authorrunning{Yung-Fu Chen \and et al.}

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published

\institute{The Ohio State University, Columbus OH 43221, USA\\
\email{chen.6655@osu.edu, weide.3@osu.edu}}

%%\toctitle{Lecture Notes in Computer Science}
%%\tocauthor{Authors' Instructions}
\maketitle

% Avoid using chapter/section number in numbering a listing
\renewcommand\thelstlisting{\arabic{lstlisting}}

% Sections

\section{Introduction}
Your final project report should include:
1. A write-up describing

(a) the design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API

(b) instructions and illustration of use, in terms of a README file and/or user guide,

(c) how your implementation has been tested,

(d) performance of your implementation,

(e) assumptions or limitations of your design,

(f) any omissions or errors in your implementation, and

(g) any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)

2. Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.

3. Script of a session showing the program under test.

\subsection{Problem Specification}
\subsection{Bus Stop Functions}

\section{Algorithm}
\subsection{Request Assignment Algorithm}

\section{Implementation}
\subsection{.NOW motes vs. Emulator}
\subsection{Software Architecture}
\subsection{Testing and Evaluation}
\subsection{Limitations, Challenges, and Omissions}
\begin{itemize}
  \item Request Generation
  \item Search for nearby buses: BFS vs. Broadcast
  \item No time synchronization---instead, use Emulator's absolute time, which is based on the host's time, which is the same for all nodes
\end{itemize}
\subsection{Using the Smart-Bus Application}

\section{Conclusion}

\newpage
\appendix
\section{Source Code}

% \bibliographystyle{abbrv}
% \bibliography{merged-bibliography,siv-bibliography,bibliography_3,bibliography_lastminute,Xiong2017Abstract} % ,weide-bibliography}

\end{document}

### 2019-04-19 Report/paper.tex
Deleted spurious comments in llncs template
Added prose to Implementation section

@@
 \section{Implementation}
+This in-situ bus scheduling algorithm was implemented in C\# using the .NET Microframework. It makes use of the Samraksh Emulator to simulate a (potentially large) network of buses and bus stops.
+
 \subsection{.NOW motes vs. Emulator}
+This project was implemented on the Samraksh Emulator, not .NOW motes.
+The reasons for thei are varied, but one deciding factor was a lack of availability of motes to use in testing and demonstration.
+Because this project was built as part of the curriculum for a semester-long class, the developers had access to at most three motes.
+Unfortunately, any interestin gdemonstration of the algorithm involves at least three bus stops and two buses; that is, five motes would have ben an absolute minimum to showcase the capabilities of this algorithm.
+Thus, the devision was made to implement the project using the Samraksh Emulator, of which arbitrarily many instances can be launched to simulate an arbitrarily large network.
+Using the emulator instead of motes also enabled some simplifications to the protocol which made it possible to produce a high-quality project in the time allotted.
+\subsubection{Simplifications}
+First, by eliminating many distinct pieces of hardware from the equation and consolidating them into instances of an emulator running on a host machine, the system can simplify its timekeeping.
+Rather than implementing a distibuted time synchronization algorithm, the system can rely on the host's clock to keep time.
+
+Second, by foregoing a physically distributed network of nodes with relatively weak radios and antennae, all messages became broadcasts (at least when it was convenient).
+The emulator's networking capabilities enforce that all messages are broadcast to all other nodes, but in cases where a peer-to-peer communication was desired, the broadcast message was annotated with several pieces of metadata: the kind of message it is, the originating node, and the intended destination node.
+Instances of broadcasts for the sake of simplicity and convenience are documented in the source code itself, but are detailed here.
+One such instance was the response by a Bus when a Bus Stop requests its route information.
+In a ``real'' system, due to physical limitations a Bus Stop might only communicate with buses that are nearby;
+
 \subsection{Software Architecture}

### 2019-04-19 Report/paper.tex
More Prose, updated PDF
Continuing to add prose

@@
 
-%%\documentclass[runningheads,a4paper]{llncs}
 \documentclass[runningheads]{llncs}
@@
 
-%\usepackage{algorithm2e}
-%\usepackage[linesnumbered]{algorithm2e}
-%\usepackage[linesnumbered,ruled]{algorithm2e}
 \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
@@
 \newcolumntype{Y}{>{\centering\arraybackslash}X}
-
-% \renewcommand{\ttdefault}{pcr} % makes bold available in a fixed-width font (use )
 
@@
 }
-
-%%\usepackage{url}
-%%\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
-%%\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
-%%\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|
-%%\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-%%\noindent\keywordname\enspace\ignorespaces#1}
 
@@
 This project was implemented on the Samraksh Emulator, not .NOW motes.
-The reasons for thei are varied, but one deciding factor was a lack of availability of motes to use in testing and demonstration.
+The reasons for this are varied, but one deciding factor was a lack of availability of motes to use in testing and demonstration.
 Because this project was built as part of the curriculum for a semester-long class, the developers had access to at most three motes.
@@
 Using the emulator instead of motes also enabled some simplifications to the protocol which made it possible to produce a high-quality project in the time allotted.
-\subsubection{Simplifications}
+
+\subsubsection{Simplifications}
 First, by eliminating many distinct pieces of hardware from the equation and consolidating them into instances of an emulator running on a host machine, the system can simplify its timekeeping.
@@
 Instances of broadcasts for the sake of simplicity and convenience are documented in the source code itself, but are detailed here.
+
 One such instance was the response by a Bus when a Bus Stop requests its route information.
-In a ``real'' system, due to physical limitations a Bus Stop might only communicate with buses that are nearby;
+In a ``real'' system, due to physical limitations a Bus Stop might only communicate with buses that are nearby; a breadth-first search approach could be used to (eventually) retrieve information about all buses.
+In our proof-of-concept, each bus will always respond to a broadcast from a stop asking for route information.
+
+Another instance where the broadcast nature of messages was taken advantage of was in the simulation start-up phase.
+The \lstinline{RequestDriver} process, upon start up, broadcasts to all nodes in the network the absolute time at which it began sending requests.
+This is used by each other process as the reference to determine how much simulated time has passed, in order to, for example, determine a bus's current location along its route.
+
+Another simplification enabled by the decision to use the Emulator is that one instance can be reserved as the ``passengers''.
+Since each node in the Emulator network can communicate with all the others, a single instance can simulate the requests from many different passengers to many different bus stops.
+A detailed discussion of the behavior of passengers in our system appears in Section~\ref{sub:passengers}.
 
 \subsection{Software Architecture}
+Designing the software structure to make use of multiple instances of the Emulator was a focus at the beginning of the project.
+The structure of the software project is as follows.
+Each ``kind'' of process (i.e., Bus, Bus Stop, and Passenger(s)) lives in its own C\# \emph{project}, housed within the Smart Bus \emph{solution}.
+There are 4 total projects in the solution: \lstinline{Bus}, \lstinline{Bus-Stop}, \lstinline{Request-Driver}, and \lstinline{Utilities And Classes}.
+The first three, of course, represent the entities involved in the network itself.
+The fourth project, Utilities And Classes, holds all common components used by the other three projects, including representations of \lstinline{Bus}, \lstinline{BusStop}, and \lstinline{Request}.
+
+Each entity-specific project is composed primarily of a single class, the Driver.
+The Driver contains an instance of the appropriate entity.
+The Driver is responsible for sending appropriate messages to the network, and for handling the receipt of messages from the network.
+
+\subsection{Message Structure}
+Due to the broadcast nature of the Emulator network capabilities, it was necessary to define a relatively complex structure for the messages, which include the originating node, the destination node (if any), the kind of message, and any data associated with the message.
+There was also a need for the developers to agree upon this structure.
+
+The final project contains a suite of classes relating to messaging in this system.
+The primary class is \lstinline{SBMessage}, which defines the overall structure of a message and provides a utility to broadcast the message.
+
+Also required was an interface, \lstinline{IMessagePayload}, to be implemented by any component which might need to be included in a message in this system.
+Such components include \lstinline{Route}, \lstinline{DateTime},\footnote{A payload with type \lstinline|DateTime| is actually a wrapper type, \lstinline|PayloadDateTime| due to C\# restrictions on extending \lstinline|struct|s.} \lstinline{Request}, and others.
+
 \subsection{Testing and Evaluation}
 \subsection{Limitations, Challenges, and Omissions}
-\begin{itemize}
-  \item Request Generation
-  \item Search for nearby buses: BFS vs. Broadcast
-  \item No time synchronization---instead, use Emulator's absolute time, which is based on the host's time, which is the same for all nodes
-\end{itemize}
+\subsubsection{Passenger Behavior}
+\label{sub:passengers}
+Initially, the plan for simulating passengers was to randomly generate requests on the fly, which would be served and assigned by appropriate bus stops.
+However, the inherent limitations of the .NET Microframework proved insurmountable given the relatively short time frame.
+
+In lieu of dynamic passenger requests, a \lstinline{RequestPattern} interface was devised which permits the arbitrary, static instantiation of passenger requests, to be processed in real-time by the \lstinline{RequestDriver} Emulator instance.
+For each request in the pattern, the driver schedules a timer to fire at the time when that passenger is intended to dispatch the request.
+However, the \lstinline{RequestPattern} interface is general enough that an implementation could, theoretically, generate random requests on the fly, though that implementation does not appear in this project.
+
 \subsection{Using the Smart-Bus Application}

### 2019-04-19 Report/paper.tex
Added prose, fixed a comment in SBMessage

@@
 \section{Implementation}
-This in-situ bus scheduling algorithm was implemented in C\# using the .NET Microframework. It makes use of the Samraksh Emulator to simulate a (potentially large) network of buses and bus stops.
+This in-situ bus scheduling algorithm was implemented in C\# using the .NET Microframework.
+It makes use of the Samraksh Emulator to simulate a (potentially large) network of buses and bus stops, as well as a sequence of passenger requests.
 
@@
 Because this project was built as part of the curriculum for a semester-long class, the developers had access to at most three motes.
-Unfortunately, any interestin gdemonstration of the algorithm involves at least three bus stops and two buses; that is, five motes would have ben an absolute minimum to showcase the capabilities of this algorithm.
-Thus, the devision was made to implement the project using the Samraksh Emulator, of which arbitrarily many instances can be launched to simulate an arbitrarily large network.
+Unfortunately, an interesting demonstration of the algorithm involves at least three bus stops and two buses; that is, five motes would have been the minimum to showcase the capabilities of this algorithm.
+Thus, the decision was made to implement the project using the Samraksh Emulator, of which arbitrarily many instances can be launched to simulate an arbitrarily large network.
 Using the emulator instead of motes also enabled some simplifications to the protocol which made it possible to produce a high-quality project in the time allotted.
@@
 
-Second, by foregoing a physically distributed network of nodes with relatively weak radios and antennae, all messages became broadcasts (at least when it was convenient).
-The emulator's networking capabilities enforce that all messages are broadcast to all other nodes, but in cases where a peer-to-peer communication was desired, the broadcast message was annotated with several pieces of metadata: the kind of message it is, the originating node, and the intended destination node.
+Second, by foregoing a physically distributed network of nodes with relatively weak radios and antennae, all messages can be broadcasts (when it is convenient).
+The emulator's networking capabilities enforce that all messages are broadcast to all other nodes, but in cases where a peer-to-peer communication is desired, the broadcast message is annotated with several pieces of metadata: the kind of message it is, the originating node, and the intended destination node.
 Instances of broadcasts for the sake of simplicity and convenience are documented in the source code itself, but are detailed here.
 
-One such instance was the response by a Bus when a Bus Stop requests its route information.
+One such instance is the response by a Bus when a Bus Stop requests its route information.
 In a ``real'' system, due to physical limitations a Bus Stop might only communicate with buses that are nearby; a breadth-first search approach could be used to (eventually) retrieve information about all buses.
@@
 
-Another instance where the broadcast nature of messages was taken advantage of was in the simulation start-up phase.
+Another instance where the broadcast nature of messages is taken advantage of is in the simulation start-up phase.
 The \lstinline{RequestDriver} process, upon start up, broadcasts to all nodes in the network the absolute time at which it began sending requests.
@@
 \subsection{Message Structure}
-Due to the broadcast nature of the Emulator network capabilities, it was necessary to define a relatively complex structure for the messages, which include the originating node, the destination node (if any), the kind of message, and any data associated with the message.
-There was also a need for the developers to agree upon this structure.
+Due to the broadcast nature of the Emulator network capabilities and a lack of support for peer-to-peer communication, it was necessary to define a relatively complex structure for the messages, which include the originating node, the destination node (if any), the kind of message, and any data associated with the message.
 
@@
 The primary class is \lstinline{SBMessage}, which defines the overall structure of a message and provides a utility to broadcast the message.
+
+\begin{lstlisting}[label=lst:sbmessage,caption={Source code for the \lstinline|SBMessage| class}]
+public class SBMessage
+{
+    public struct MessageSource
+    {
+        public enum SourceType
+        {
+            BROADCAST = 0,
+            PASSENGER = 1,
+            BUS_STOP = 2,
+            BUS = 3
+        }
+        public SourceType srcType;
+        public int srcId;
+
+        // Initializer defaults to BROADCAST with no id
+        public MessageSource(string srcType = "0", string srcId = "-1")
+        {
+            this.srcType = (SourceType)int.Parse(srcType);
+            this.srcId = int.Parse(srcId);
+        }
+
+        public MessageSource(SourceType srcType = SourceType.BROADCAST, int srcId = -1)
+        {
+            this.srcType = srcType;
+            this.srcId = srcId;
+        }
+
+        public override string ToString()
+        {
+            return this.srcType.ToString() + " " + this.srcId.ToString();
+        }
+    }
+
+    public struct MessageHeader
+    {
+        public const int Length = 5;
+
+        public MessageType type;
+        public MessageSource origin;
+        public MessageSource destination;
+
+        public MessageHeader(MessageType type, MessageSource origin, MessageSource destination)
+        {
+            this.type = type;
+            this.origin = origin;
+            this.destination = destination;
+        }
+
+        public override string ToString()
+        {
+            return type.ToString() + " " + origin.ToString() + " " + destination.ToString();
+        }
+    }
+
+    public enum MessageType
+    {
+        START_SIMULATION = 10,
+        SEND_PASSENGER_REQUEST = 11,
+
+        ROUTE_INFO_REQUEST = 20,
+        ROUTE_INFO_RELAY_REQUEST = 21,
+        ROUTE_CHANGE_REQUEST = 22,
+        REQUEST_SCHEDULED = 23,
+
+        ROUTE_INFO_RESPONSE = 30,
+        ROUTE_CHANGE_ACK = 31
+    }
+
+    public MessageHeader header;
+    public IMessagePayload payload;
+
+    public SBMessage() { }
+
+    public SBMessage(MessageType type, MessageSource origin, MessageSource destination, IMessagePayload payload)
+    {
+        this.header = new MessageHeader(type, origin, destination);
+        this.payload = payload;
+    }
+
+    public SBMessage(string msgString)
+    {
+        string[] components = msgString.Split();
+        MessageType msgType = (MessageType)int.Parse(components[1]);
+        MessageSource source = new MessageSource(components[1], components[2]);
+        MessageSource destination = new MessageSource(components[3], components[4]);
+        int headLength = MessageHeader.Length;
+        switch (msgType)
+        {
+                // Message from Passenger
+            case MessageType.START_SIMULATION:
+                this.payload = new PayloadDateTime(components, ref headLength);
+                break;
+            case MessageType.SEND_PASSENGER_REQUEST:
+                this.payload = new Request(components, ref headLength);
+                break;
+
+                // Message from Bus Stop
+            case MessageType.ROUTE_INFO_REQUEST:
+                this.payload = new PayloadSimpleString();
+                break;
+            case MessageType.ROUTE_INFO_RELAY_REQUEST:
+                this.payload = new PayloadRouteRequestForward(components, ref headLength);
+                break;
+            case MessageType.ROUTE_CHANGE_REQUEST:
+                this.payload = new Route(components, ref headLength);
+                break;
+            case MessageType.REQUEST_SCHEDULED:
+                this.payload = new Request(components, ref headLength);
+                break;
+
+                // Message from Bus
+            case MessageType.ROUTE_INFO_RESPONSE:
+                this.payload = new Route(components, ref headLength);
+                break;
+            case MessageType.ROUTE_CHANGE_ACK:
+                this.payload = new PayloadRouteChangeAckResponse(components, ref headLength);
+                break;
+        }
+    }
+
+    public override string ToString()
+    {
+        StringBuilder msg = new StringBuilder();
+        msg.Append(this.header.ToString() + " ");
+        msg.Append(this.payload.BuildPayload());
+        return msg.ToString();
+    }
+
+    public void Broadcast(NetInst NetPort)
+    {
+        Debug.Print("Sending message " + this.ToString());
+        byte[] msgBytes = Utilities.StringToByteArray(this.ToString());
+        NetPort.Broadcast(msgBytes, msgBytes.Length);
+    }
+}
+\end{lstlisting}
 

### 2019-04-19 Report/paper.tex
More prose

--- 2019-04-19 Report/paper.tex
@@
 Because this project was built as part of the curriculum for a semester-long class, the developers had access to at most three motes.
-Unfortunately, any interestin gdemonstration of the algorithm involves at least three bus stops and two buses; that is, five motes would have ben an absolute minimum to showcase the capabilities of this algorithm.
-Thus, the devision was made to implement the project using the Samraksh Emulator, of which arbitrarily many instances can be launched to simulate an arbitrarily large network.
+Unfortunately, an interesting demonstration of the algorithm involves at least three bus stops and one bus.
+Evaluating the efficacy and scalability of the algorithm with such a limited number of nodes would be impossible.
+Thus, the decision was made to implement the project using the Samraksh Emulator, of which arbitrarily many instances can be launched to simulate an arbitrarily large network.
 Using the emulator instead of motes also enabled some simplifications to the protocol which made it possible to produce a high-quality project in the time allotted.
@@
 Also required was an interface, \lstinline{IMessagePayload}, to be implemented by any component which might need to be included in a message in this system.
-Such components include \lstinline{Route}, \lstinline{DateTime},\footnote{A payload with type \lstinline|DateTime| is actually a wrapper type, \lstinline|PayloadDateTime| due to C\# restrictions on extending \lstinline|struct|s.} \lstinline{Request}, and others.
+Such components include \lstinline{Route}, \lstinline{DateTime},\footnote{A payload with type \lstinline|DateTime| is enclosed by a wrapper type, \lstinline|PayloadDateTime| due to C\# restrictions on extending \lstinline|struct|s.} \lstinline{Request}, and others.
 
-\subsection{Testing and Evaluation}
 \subsection{Limitations, Challenges, and Omissions}
@@
 
-\subsection{Using the Smart-Bus Application}
+\subsection{Testing and Evaluation}
+The efficacy of this (admittedly complicated) distributed algorithm versus a naive, static scheduling approach was evaluated.
+The static scheduling approach is similar to that employed by real public bus systems in the world: there are $n$ buses, each with a predetermined route $R$ through a number of stops.
+
+Evaluation metrics include
+\begin{itemize}
+	\item The number of buses required to service $k$ passenger requests on time (lower is better)
+	\item The number of requests that can be served on time with $n$ buses (higher is better)
+\end{itemize}
+
+\subsubsection{Specification of Static Approach}
+
+\subsubsection{Request Patterns}
+A variety of request patterns were used for evaluation. The scales of these patterns range from two passengers to ???, from three bus stops to ???, and from two buses to ???.
+
+\section{Using the Smart-Bus Application}
+There are several steps to running the application:
+\begin{itemize}
+	\item Launch $n$ instances of \lstinline{Bus-Driver}
+	\item Launch $m$ instances of \lstinline{Bus-Stop-Driver}
+	\item Ensure the simulation parameters of \lstinline{Request-Driver} match the number of buses and stops that have been launched
+	\item Launch an instance of \lstinline{Request-Driver} with the requisite simulation parameters (i.e., Request Pattern and Time Multiplier)
+	\item Wait for simulation to conclude
+\end{itemize}
+
+\subsection{Extending the Smart-Bus Application}
+It is, of course, possible to extend or improve the functionality of this application in many ways.
+\begin{itemize}
+	\item For work on generating dynamic requests, implement the \lstinline{RequestPattern} interface 
+	\item To change the request assignment behavior, modify the \lstinline{BusStop} class in \lstinline{Utilities and Classes}
+	\item To implement breadth-first search to find buses, modify the \lstinline{BusStopDriver} class
+	\begin{itemize}
+		\item Changes to \lstinline{Bus} will also be necessary to restrict its responses to those stops within its immediate vicinity
+	\end{itemize}
+\end{itemize}
 

### 2019-04-19 Smart-Bus/Utilities/Request.cs
Update Request.cs

@@ -14,6 +14,7 @@ namespace Smart_Bus
         public BusStop origin;
         public BusStop destination;
         public bool served;
+        public bool delay;
 
         public Request(int earliestPickupTime, int latestDeliveryTime, int origin, int destination)
         {

### 2019-04-19 Bus-Stop/BusStopUniTest.cs
Update BusStopUniTest.cs

@@ -25,7 +25,7 @@ namespace Smart_Bus
             stop_1.update_receive(bus[0], true);
 
             //assing request to stop1
-            stop_1.request_receive(requests[0]);
+            stop_1.request_receive(requests[0], false);
 
             //update bus1 info to stop1
             bus[0].routeInfo = new Request_v[2];
@@ -44,7 +44,7 @@ namespace Smart_Bus
 
             //update bus1 info to stop1
             stop_1.update_receive(bus[1], true);
-            stop_1.request_receive(requests[1]);
+            stop_1.request_receive(requests[1], false);
             
         }
     }

### 2019-04-19 Smart-Bus/Utilities/Bus.cs
Update Bus.cs
Commented out routeInfo from Bus.cs (it is now rolled into Route

@@ -15,7 +15,7 @@ namespace Smart_Bus
         public int busStartTime; //ts_k: expected start time at terminus 
         public int busEndTime; //te_k: expected end time terminus
         public Route route;
-        public Request_v[] routeInfo;
+        //public Request_v[] routeInfo;
 
         public Bus(int id, int terminusId, int busStartTime, int busEndTime)
         {

### 2019-04-19 Bus-Stop/BusStopDriver.cs
Merging

@@ -1,0 +1,118 @@
+using System;
+using System.Text;
+using Microsoft.SPOT;
+using System.Threading;
+using Microsoft.SPOT.Hardware;
+using Microsoft.SPOT.Messaging;
+using System.IO.Ports;
+using Samraksh.SPOT.Emulator.Network;
+
+namespace Smart_Bus
+{
+    class BusStopDriver
+    {
+        private static int getRealSendTime(int simulationMillis)
+        {
+            return simulationMillis / Constants.TIME_MULTIPLIER;
+        }
+
+        private static BusStopDriver instance;
+
+        // Requires an id, which is equivalent to appId, so do not create bus until after appId is initialized
+        BusStop myBusStop;
+
+        NetInst NetPort;
+        NetInst.ReceivePktCallback rcvcallBack;
+
+        private static UInt16 appId;
+        private static DateTime SimStart;
+        private const int NearbyThreshold = 1;
+
+        private BusStopDriver()
+        {
+            rcvcallBack = new NetInst.ReceivePktCallback(ReadNetworkPkt);
+            NetPort = new NetInst(rcvcallBack);
+        }
+
+        public static BusStopDriver getInstance()
+        {
+            if (BusStopDriver.instance == null)
+            {
+                BusStopDriver.instance = new BusStopDriver();
+            }
+            return BusStopDriver.instance;
+        }
+
+        public static void ReadNetworkPkt(byte[] msg, int size)
+        {
+
+            string msgString = Utilities.ByteArrayToString(msg);
+            SBMessage message = new SBMessage(msgString);
+            Debug.Print("Received message: " + msgString);
+            SBMessage.MessageType msgType = message.header.type;
+            BusStop stop = BusStopDriver.getInstance().myBusStop;
+
+            switch (msgType)
+            {
+                case SBMessage.MessageType.START_SIMULATION:
+                    {
+                        BusStopDriver.SimStart = ((PayloadDateTime)message.payload).date;
+                        Utilities.SimStart = BusStopDriver.SimStart;
+                        instance.myBusStop.SimStart = BusStopDriver.SimStart;
+                        break;
+                    }
+                case SBMessage.MessageType.SEND_PASSENGER_REQUEST:
+                    {
+                        Request new_request = (Request)message.payload;
+
+                        //If the bus stop does not have any busInfo, it has to send ROUTE_INFO_REQUEST first
+                        if (instance.myBusStop.busInfo_list == null)
[…]

### 2019-04-19 Smart-Bus/Utilities/BusStop.cs

@@ -4,42 +4,90 @@ using Microsoft.SPOT;
 using System.Collections;
 
 namespace Smart_Bus
-{
+{   
     public class BusStop
     {
         public int id;
         public Bus[] busInfo_list;
         public Request[] request_list;
-        public const int urgencyThreshold = 100;
+        public const int urgencyThreshold = 300000; //5 minutes
+        public DateTime SimStart;
 
         public BusStop(int id)
         {
             this.id = id;
         }
-        
-        public void request_receive(Request new_request)
+
+        public void request_receive(Request new_request, bool delay)
         {
+            TimeSpan elapsedTime = DateTime.Now - SimStart;
+            int simulationMillis = (int)elapsedTime.Milliseconds;
+
             Debug.Print("Received new request");
             Debug.Print("Origin: " + new_request.origin.id + ", Destination: " + new_request.destination.id);
             Debug.Print("EarliestPickupTime: " + new_request.earliestPickupTime + ", LatestPickupTime: " + new_request.latestPickupTime);
             Debug.Print("EarliestDeliveryTime: " + new_request.earliestDeliveryTime + ", LatestDeliveryTime: " + new_request.latestDeliveryTime);
 
-            //First, add the new request to the request list
-            this.request_list = Append_request(new_request);
+            
+
+            if (delay == true)
+            {
+                new_request.delay = true;
+                //First, add the new request to the request list
+                this.request_list = Append_request(new_request);
+
+                new Timer(new TimerCallback(request_delay_timer_handler), null, 5000, 0);
+                return;
+            }
+            else
+            {
+                new_request.delay = false;
+                //First, add the new request to the request list
+                this.request_list = Append_request(new_request);
+            }
 
             //Second, assign the new request immediately if (latestDeliveryTime - current time) < urgencyThreshold
-            //if (new_request.latestDeliveryTime - Global_Timer.C_Time < urgencyThreshold)
+            if (new_request.latestDeliveryTime - simulationMillis < urgencyThreshold)
             {
                 request_assign(new_request);
             }
             //otherwise, start a timer with the period of latestDeliveryTime - (current time + urgencyThreshold),
             // assign the new request when the timer timeout
-            //else
+            else
             {
-                request_assign(new_request);
[…]

### 2019-04-19 Smart-Bus/Utilities/Constants.cs

@@ -7,10 +7,11 @@ namespace Smart_Bus
     {
         // Every hop between bus stops is constant; for this demo, it takes 1 simulated minute
         public static readonly int HOP_DURATION = 60000;
+        public static readonly int STOP_DURATION = 10000;
 
         // 1 is Real Time (i.e., one second of wall time per second of simulation time)
         // Suggested values are on the order of 100 (every 10 milliseconds of wall time is one second of simulation time)
-        public static readonly int TIME_MULTIPLIER = 1;
+        public static readonly int TIME_MULTIPLIER = 100;
 
         // DateTime format string for all messages
         public static string DATE_TIME_FORMAT = "yyyy'-'MM'-'dd'T'H':'mm':'ss.fff";

### 2019-04-19 Smart-Bus/Utilities/Request.cs

@@ -6,6 +6,12 @@ namespace Smart_Bus
 {
     public class Request : IComparable, IMessagePayload
     {
+        // TODO: Refactor to Pair of Request_v
+        //public int sendTime;
+        //public Request_v origin;
+        //public Request_v dest;
+        //public bool delay;
+
         public int requestSendTime;
         public int earliestPickupTime;
         public int latestPickupTime;
@@ -14,6 +20,7 @@ namespace Smart_Bus
         public BusStop origin;
         public BusStop destination;
         public bool served;
+        public bool delay;
 
         public Request(int earliestPickupTime, int latestDeliveryTime, int origin, int destination)
         {

### 2019-04-19 Smart-Bus/Utilities/SBMessage.cs

@@ -23,7 +23,7 @@ namespace Smart_Bus
             public SourceType srcType;
             public int srcId;
 
-            // Initializer defaults to PASSENGER with no id
+            // Initializer defaults to BROADCAST with no id
             public MessageSource(string srcType = "0", string srcId = "-1")
             {
                 this.srcType = (SourceType)int.Parse(srcType);

### 2019-04-20 Bus/BusDriver.cs
Bus now accepts less info from Stop on ROUTE_CHANGE_REQUEST
Bus accepts two parallel arrays; Request_v[] and int[], where the Request_v[] is each "important stop" along the route (that is, those with a pickup or dropoff) and the int[] is the sequence of requestIds served by the route.

Format for this message TBD

@@ -109,8 +109,14 @@ namespace Smart_Bus
                     }
                 case SBMessage.MessageType.ROUTE_CHANGE_REQUEST:
                     {
-                        Route other = (Route)message.payload;
+                        //Route other = (Route)message.payload;
+                        Request_v[] requests = new Request_v[4];
+                        int[] requestIds = new int[4];
                         IMessagePayload replyPayload;
+
+                        bus.UpdateServedRequests();
+
+                        Route other = new Route(requests, requestIds);
 
                         // I believe the only way we might end up with the else case here
                         //  is if another stop has changed our route since this stop last
@@ -120,7 +126,8 @@ namespace Smart_Bus
                             // If this is an acceptable route to change to, 
                             //  then set our route and notify the stop
                             bus.route = other;
-                            replyPayload = new PayloadRouteChangeAckResponse(true, other);
+
+                            replyPayload = new PayloadRouteChangeAckResponse(true, bus.route);
                         }
                         else
                         {

### 2019-04-20 Report/paper.tex
Update paper.tex
Add chapter 1 (introduction) and 2 (problem specification)

@@
 
-\subsection{Problem Specification}
-\subsection{Bus Stop Functions}
+Internet of Things (IoT) has been an innovative technology connecting heterogeneous devices to form a practical network for facilitation of human work.
+In IoT, mobile ad‐hoc network (MANET) is a key point to give the greater mobility for users and reduce deployment costs of the network.
+Typically, Wi-Fi and IEEE 802.15.4 are the popular communication technologies for different application requirements.
+Wi-Fi technique provides good throughput in wireless communication but limited transmission range.
+On the other hand, although IEEE 802.15.4 supports low data rate with available range of dozens of meters, it has the property of low cost and low power consumption.
+However, there are applications requiring data traffic routing in a wide area of a few kilometers.
+For example, in fleeting tracking system, each car is regarded as a mobile node in a MANET.
+The average hop distance between two adjacent nodes could be in kilometers.
+Thus, it is infeasible to adopt Wi-Fi or IEEE 802.15.4 techniques to guarantee the connectivity of network in such application.
+Thus, several transmission technologies have been introduced to satisfy the requirement of long transmission range.
+Low-Power Wide-Area Network (LPWAN) is a type of wireless telecommunication wide area network designed to allow long range communications at a low bit rate among connected objects with battery power.
+Like Long-Range (LoRa) technology, it is a LPWAN specification intended for wireless battery-operated objects and suitable for these applications.
+
+Due to the maturity and popularization of Wi-Fi in mobile devices rather than the technology of LPWAN, we proposed an idea to take advantage of both Wi-Fi and LPWAN and combine them into an access point in MANET, so that mobile devices, such as cellphones and tablets, can directly use Wi-Fi to access the network via this kind of access point.
+Also, because of the property of LPWAN, the hop distance between neighbor access points can be long enough to reduce the hop count in routing.
+Moreover, we will introduce an innovative application, named Smart Bus System to show how the whole network composed by this kind of access points can support low data traffic, energy efficiency, dynamic scheduling, and efficient routing.
+Also, this paper aims to propose a distributed algorithm which efficiently solves the bus scheduling problem in the smart bus system so that the total travel time, sum of lateness over all pick-up and delivery locations, and sum of overtime over all buses can be minimized.
+\subsection{Smart Bus System}
+Compared to typical bus system with fixed route, a smart bus system is required for dynamically calculating the route to pick up passengers and efficiently shorten the regular route to save more waiting time of passengers as well as energy consumption of buses.
+We proposed low power Bus Service Access Points (BSAPs) with Wi-Fi and LPWAN to establish a mobile ad-hoc network with the ability to provide high speed transmission in short distance below 30 meters and low speed transmission in long distance in kilometers.
+In this system, each bus and bus stop are equipped with one BSAP.
+A BSAP can offer limited Wi-Fi service for pick-up service and browser-based application for user to send a request or query service information.
+A passenger with cell phone can directly use Wi-Fi to access the BSAP to send a request for pick-up service at any bus stop on campus.
+The request includes the passenger’s origin stop, destination stop, the earliest departure time from origin and the latest arrival time to destination.
+After receiving a request, the serving bus stop needs to determine the matched bus according to the pair of pick-up and delivery stops and its time constraints.
+On the other hand, after receiving a request, a BSAP on bus has to determine whether to serve the passenger or not.
+If the bus accepts this request, it will recalculate a new route to pick up a set of passengers and satisfy their expected arrival time as possible.
+Otherwise, if the bus rejects the request due to it limited capacity, the corresponding serving bus stop has to reassign the request to other available buses for seeking the best utilization.
+
+Without attaching an additional LPWAN interface, a passenger will always use Wi-Fi radio to communicate with a BSAP on bus or bus stop.
+On the other side, a BSAP can exploit the Wi-Fi interface with higher throughput to transmit message if the distance between two neighbor BSAPs is within an available Wi-Fi range.
+Otherwise, a BSAP can always use LPWAN radio to communicate with any neighbor BSAPs due to its long transmission range in kilometers.
+We assume all BSAPs on bus stops form a static connected network.
+Thus, the mobile BSAPs on any buses moving within the area of static connected network can still be under the network coverage so that the matched bus can always received the request from bus stops regardless of its location.
+
+\section{Problem Specification}
+In this bus system, a passenger will send the adjacent bus stop a request including his origin stop, destination stop, the earliest departure time from origin and the latest arrival time to destination.
+Hence, to implement the system and meet the requirement from passengers, we need to solve the scheduling problem stated in the following sections.
+\subsection{Scheduling Problem}
+Let $p_i^+$ and $p_i^-$ respectively denote the pickup point and the delivery point of passenger i.
+Also, we have earliest departure time $ED_i$ from point $p_i^+$, latest arrival time $LA_i$ to point $p_i^-$.
+The problem consists of a set $B = \{1, 2, …, m\}$ of m buses in the smart bus network with their current routes.
+For the route of bus k, it includes a combination of multiple pickup points and deliver points, which is denoted by $R_k = \{p_0, p_1, …, p_r\}$, where $p_i^+\in R_k$ if passenger i is matched to bus k and he has not been picked up and $p_i^-\in R_j$ if passenger i is matched to bus k and he has not reached his destination.
+The order of points in $R_k$ depends on the earliest departure time and the latest arrival time of matched passengers to bus k.
+If p is the number of matched passengers to bus k who have not been picked up and q is the number of matched passengers to bus k who have not reached their destinations.
+Thus, p must be equal to or greater than q.
+This is because there probably exist some passengers who have been picked up but not reached their destinations.
+For a bus k, it has limited capacity to serve passengers.
+Assume all buses in the network have the same capacity.
+Let $c_{k,v}$ be the number of seat available in bus k when arriving location v.
+$c_{k,v}$ decreases by 1 after serving location v which belongs a pickup location.
+Otherwise, $c_{k,v}$ increase by 1 after serving a delivery location.
+A bus k cannot serve any passengers at a pickup location v if $c_{k,v}$ is 0.
+
+Moreover, let $t_{a,b}$ be the direct travel time between points a and b.
+For each service location v (pickup or delivery point), we compute time windows of this service location $[e_v, l_v]$, which denotes the earliest and latest served time.
+For example, for a request i with pickup point $p_i^+$ and delivery point $p_i^-$, we can calculate the time window of $p_i^+$, $[ED_i, LA_i – t_{p_i^+,p_i^-}]$ and the time window of $c_i^-$, $[ED_i + t_{p_i^+,p_i^-}, LA_i]$.
+In the system, each bus starts and ends its route at the bus terminus (location 0).
+Let $ts_k$ and $te_k$ denote start time and end time for bus k.
+There is also a time window at the terminus, where $e_0$ and $l_0$ are the earliest start time and latest end time of each route.
+
+Let $t_v$ denote the serving time at point v by the matched bus.
+It denotes the exact pick or delivery times for passengers.
+If v’ is the predecessor of v in a route, the arrival time of the bus k at v is $t_v = max(t_{v’}, e_{v’}) + t_{v’, v}$; otherwise $t_v$ = $ts_k$ + $t_{0, v}$.
+Since the requests from passengers are dynamic and independent, the problem is to find a matched bus for a newly added passenger in real time while the system receives a request from him and to readjust the route of the matched bus in order to minimize total travel time of buses, sum of lateness over all pick-up and delivery locations, and sum of overtime over all buses.
+Thus, we can define the problem as the statement provided below:
+
+Given a set $B = \{1, 2, …, m\}$ of m buses on the route.
+Each bus k has the current route $R_k = \{p_0, p_1, …\}$.
+Whenever receiving a request from passenger i with the parameters $p_i^+$, $p_i^-$, $ED_i$, and $LA_i$, we compute the matched bus and insert the pickup point $p_i^+$ and delivery point $p_i^-$ to the route $R_j$ of matched bus j according to the time windows of service location $[e_v, l_v]$.
+The goal is to minimize the objective function:
+
+\begin{equation}
+min\{\sum_{k\in B}{T_k} + \alpha\sum_{v\in V}{max\{0, t_v - l_v\}} + \beta\sum_{k\in B}{max\{0, te_k - l_0\}} \}
+\end{equation}
+
+$T_k$ denotes the total travel time of bus k. The weights $\alpha$ and $\beta$ define the relative importance of the different components.
 

### 2019-04-20 Report/paper.tex
add chapter 1, 2, and 3

@@
 \section{Algorithm}
+\subsection{Route Flexibility}
+Since the goal is to minimize the objective function, whenever assigning requests from passenger, a serving bus stop needs to compare a metric of buses to select the best bus leading to the minimized result of objective function.
+Thus, we define a metric, route flexibility, to evaluate the flexibility to accommodate a new request into the current route.
+Let $f_{k,v}$ denote the flexible time of  bus k at location v, which is defined by $l_v – t_v$.
+That is to say, if the arrival time tv is much smaller than the latest served time $l_v$, then the bus has the higher flexibility to accept more requests.
+Hence, to calculate the route flexibility, we use $F_k$ to denote the accumulated flexible time of service locations in $R_k$.
+
+\begin{equation}
+F_k = \sum_{v\in R_k}{f_v} + (l_0 - te_k)
+\end{equation}
+
+$l_0 - te_k$, the flexible time at terminus, decreases or stays the same whenever a new request is added to $R_k$.
+Note that $\sum_{k\in B}{F_k}$ is inversely proportional to objective function.
+Hence, objective function can be minimized if the total route flexibility is maximized during request assigning for each bus stop.
+\subsection{Route Information Sharing}
+When assigning requests, the serving bus stop must know the current route information of buses and their current capacity.
+For example, if bus k picked up a passenger at location v, then the number of service location in $R_k$ decreased and the capacity $c_k$ decreased as well.
+At that time, bus k should update the information to bus stops.
 \subsection{Request Assignment Algorithm}
+With the route information of buses, a bus stop is able to compare the route flexibility of different buses after inserting a request to their routes.
+However, when receiving a new request, instead of immediately assigning it to a bus, the serving bus stop will wait for a certain to determine which request should be served first and which bus is the best one to serve the request.
+This is because all requests are dynamically launched by passengers, bus stops do not know requests in advance until receiving them.
+To maximize the total flexibility as possible, bus stops should serve requests according to the urgency rather than the receiving order since we know an urgent request can harm the route flexibility if it is not immediately assigned to a bus.
+On the other hand, the request, with larger latest arrival time, can be reasonably delayed for a certain time because buses may need to reserve space for the potentially future urgent request.
+
+Let $\delta$ denote the urgent threshold.
+For a request i, if $LA_i - \delta$ is smaller than the current time, we can say it is an urgent request.
+For assigning urgent requests, a serving bus stop assign the request to the bus with maximal route flexibility after inserting the request.
+All other requests will not be assigned until all urgent requests have been dispatched to the matched buses.
+Furthermore, for non-urgent requests, if there exists a request with $p_i^+$ and $p_i^-$ matching the service locations in current route $R_k$ of bus k, the serving bus stop will prioritize the request to be served first.
+The flexible time at terminus $(l_0 – te_k)$ remains the same after inserting this request.
+Thus, the flexibility will not be harmed.
 

### 2019-04-20 Bus/BusDriver.cs
Refactored some code, and filled in some missing method bodies
Renamed some parts of SBMessage, and made the header and payload fields publically readonly.

Implemented missing bodies for various Payload classes.

Finished implementing Bus's ROUTE_CHANGE_REQUEST response

@@ -6,6 +6,7 @@ using Microsoft.SPOT.Hardware;
 using Microsoft.SPOT.Messaging;
 using System.IO.Ports;
 using Samraksh.SPOT.Emulator.Network;
+using System.Collections;
 
 namespace Smart_Bus
 {
@@ -84,7 +85,7 @@ namespace Smart_Bus
                     }
                 case SBMessage.MessageType.ROUTE_INFO_REQUEST:
                     {
-                        int stopId = message.header.origin.srcId;
+                        int stopId = message.header.origin.endptId;
 
                         // Only reply if we're "nearby"
                         //  *Note: IsNearbyStop simply returns true for this project;
@@ -109,32 +110,42 @@ namespace Smart_Bus
                     }
                 case SBMessage.MessageType.ROUTE_CHANGE_REQUEST:
                     {
-                        //Route other = (Route)message.payload;
-                        Request_v[] requests = new Request_v[4];
-                        int[] requestIds = new int[4];
-                        IMessagePayload replyPayload;
+                        string[] messageComponents = msgString.Split();
+                        IList requestList = new ArrayList();
+                        int i = SBMessage.MessageHeader.Length;
+                        while (i < messageComponents.Length)
+                        {
+                            requestList.Add(new Request_v(messageComponents, ref i));
+                        }
+
+                        Request_v[] requests = new Request_v[requestList.Count];
+                        i = 0;
+                        while (requestList.Count > 0)
+                        {
+                            requests[i] = (Request_v)requestList[0];
+                            requestList.RemoveAt(0);
+                            i++;
+                        }
 
                         bus.UpdateServedRequests();
 
-                        Route other = new Route(requests);
+                        Route newRoute = new Route(requests);
+                        bool confirm = false;
 
-                        // I believe the only way we might end up with the else case here
-                        //  is if another stop has changed our route since this stop last
+                        // I believe the only way we this won't be true here is if
+                        //  another stop has changed our route since this stop last
                         //  received info about our route.
-                        if (bus.route.IsRequestSubsetOf(other))
+                        if (bus.route.IsRequestSubsetOf(newRoute))
                         {
                             // If this is an acceptable route to change to, 
-                            //  then set our route and notify the stop
-                            bus.route = other;
+                            //  then update our route
+                            bus.route = newRoute;
+                            confirm = true;
+                        }
 
[…]

### 2019-04-20 Smart-Bus/RequestDriver.cs

@@ -37,8 +37,8 @@ namespace Smart_Bus
 
         private static void BuildAndSendStartSimBroadcast(DateTime startTime)
         {
-            SBMessage.MessageSource origin = new SBMessage.MessageSource(SBMessage.MessageSource.SourceType.PASSENGER);
-            SBMessage.MessageSource destination = new SBMessage.MessageSource();
+            SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.PASSENGER);
+            SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint();
             IMessagePayload payload = new PayloadDateTime(startTime);
             SBMessage message = new SBMessage(SBMessage.MessageType.START_SIMULATION, origin, destination, payload);
             message.Broadcast(RequestDriver.getInstance().NetPort);
@@ -47,8 +47,8 @@ namespace Smart_Bus
         private static void BuildAndSendPassengerRequest(object obj)
         {
             Request req = obj as Request;
-            SBMessage.MessageSource origin = new SBMessage.MessageSource(SBMessage.MessageSource.SourceType.PASSENGER);
-            SBMessage.MessageSource destination = new SBMessage.MessageSource(SBMessage.MessageSource.SourceType.BUS_STOP, req.origin.stop.id);
+            SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.PASSENGER);
+            SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS_STOP, req.origin.stop.id);
             IMessagePayload payload = req;
             SBMessage message = new SBMessage(SBMessage.MessageType.SEND_PASSENGER_REQUEST, origin, destination, payload);
             message.Broadcast(RequestDriver.getInstance().NetPort);

### 2019-04-20 Smart-Bus/Utilities/PayloadRouteChangeAckResponse.cs

@@ -22,7 +22,7 @@ namespace Smart_Bus
 
         public string BuildPayload()
         {
-            return (didAcceptRouteChange ? "1" : "0") + " " + latestRoute.ToString();
+            return (didAcceptRouteChange ? "1 " : "0 ") + latestRoute.ToString();
         }
     }
 }

### 2019-04-20 Smart-Bus/Utilities/PayloadRouteRequestForward.cs

@@ -16,7 +16,7 @@ namespace Smart_Bus
 
         public string BuildPayload()
         {
-            throw new NotImplementedException();
+            return this.originalSource.ToString() + " " + this.numHops.ToString();
         }
     }
 }

### 2019-04-20 Smart-Bus/Utilities/PayloadSimpleString.cs

@@ -20,7 +20,7 @@ namespace Smart_Bus
 
         public string BuildPayload()
         {
-            throw new NotImplementedException();
+            return this.str;
         }
     }
 }

### 2019-04-20 Smart-Bus/Utilities/Request.cs

@@ -1,6 +1,7 @@
 using System;
 using System.Threading;
 using Microsoft.SPOT;
+using System.Text;
 
 namespace Smart_Bus
 {
@@ -20,16 +21,16 @@ namespace Smart_Bus
 
             this.requestSendTime = earliestPickupTime;
             this.origin = new Request_v(
-                requestId, 
-                earliestPickupTime, 
-                latestPickupTime, 
+                requestId,
+                earliestPickupTime,
+                latestPickupTime,
                 true,
-                originStop, 
+                originStop,
                 false);
             this.destination = new Request_v(
                 requestId,
-                earliestDeliveryTime, 
-                latestDeliveryTime, 
+                earliestDeliveryTime,
+                latestDeliveryTime,
                 false,
                 destStop,
                 false);
@@ -60,20 +61,8 @@ namespace Smart_Bus
             int earliestDeliveryTime = earliestPickupTime + TravelTime(originStop, destStop);
 
             this.requestSendTime = earliestPickupTime;
-            this.origin = new Request_v(
-                requestId, 
-                earliestPickupTime, 
-                latestPickupTime,
-                true, 
-                originStop, 
-                false);
-            this.destination = new Request_v(
-                requestId, 
-                earliestDeliveryTime,
-                latestDeliveryTime, 
-                false,
-                destStop,
-                false);
+            this.origin = new Request_v(requestId, earliestPickupTime, latestPickupTime, true, originStop, false);
+            this.destination = new Request_v(requestId, earliestDeliveryTime, latestDeliveryTime, false, destStop, false);
         }
 
         public int CompareTo(object obj)
@@ -101,11 +90,20 @@ namespace Smart_Bus
 
         public string BuildPayload()
         {
-            throw new NotImplementedException();
+            // After the header, the array is organized as follows:
+            //  [earliestPickupTime, latestDeliveryTime, origin, destination]
+            // where the times are in ms since simulation start
+
+            StringBuilder payload = new StringBuilder();
+            payload.Append(this.origin.earliestServingTime.ToString() + " ");
+            payload.Append(this.destination.latestServingTime.ToString() + " ");
+            payload.Append(this.origin.stop.id.ToString() + " ");
+            payload.Append(this.destination.stop.id.ToString() + " ");
+            return payload.ToString();
         }
     }
 
-    public struct Request_v
+    public struct Request_v : IMessagePayload
     {
[…]

### 2019-04-20 Smart-Bus/Utilities/Route.cs

@@ -284,5 +284,11 @@ namespace Smart_Bus
             RouteStop other = (RouteStop)obj;
             return this.stopId == other.stopId && this.duration == other.duration && this.capDelta == other.capDelta;
         }
+
+        // Here just to rid myself of a warning
+        public override int GetHashCode()
+        {
+            return base.GetHashCode();
+        }
     }
 }

### 2019-04-20 Smart-Bus/Utilities/SBMessage.cs

@@ -11,34 +11,34 @@ namespace Smart_Bus
 {
     public class SBMessage
     {
-        public struct MessageSource
+        public struct MessageEndpoint
         {
-            public enum SourceType
+            public enum EndpointType
             {
                 BROADCAST = 0,
                 PASSENGER = 1,
                 BUS_STOP = 2,
                 BUS = 3
             }
-            public SourceType srcType;
-            public int srcId;
+            public EndpointType endptType;
+            public int endptId;
 
             // Initializer defaults to BROADCAST with no id
-            public MessageSource(string srcType = "0", string srcId = "-1")
+            public MessageEndpoint(string endptType = "0", string endptId = "-1")
             {
-                this.srcType = (SourceType)int.Parse(srcType);
-                this.srcId = int.Parse(srcId);
+                this.endptType = (EndpointType)int.Parse(endptType);
+                this.endptId = int.Parse(endptId);
             }
 
-            public MessageSource(SourceType srcType = SourceType.BROADCAST, int srcId = -1)
+            public MessageEndpoint(EndpointType endptType = EndpointType.BROADCAST, int endptId = -1)
             {
-                this.srcType = srcType;
-                this.srcId = srcId;
+                this.endptType = endptType;
+                this.endptId = endptId;
             }
 
             public override string ToString()
             {
-                return this.srcType.ToString() + " " + this.srcId.ToString();
+                return this.endptType.ToString() + " " + this.endptId.ToString();
             }
         }
 
@@ -47,10 +47,10 @@ namespace Smart_Bus
             public const int Length = 5;
 
             public MessageType type;
-            public MessageSource origin;
-            public MessageSource destination;
+            public MessageEndpoint origin;
+            public MessageEndpoint destination;
 
-            public MessageHeader(MessageType type, MessageSource origin, MessageSource destination)
+            public MessageHeader(MessageType type, MessageEndpoint origin, MessageEndpoint destination)
             {
                 this.type = type;
                 this.origin = origin;
@@ -77,56 +77,67 @@ namespace Smart_Bus
             ROUTE_CHANGE_ACK = 31
         }
 
-        public MessageHeader header;
-        public IMessagePayload payload;
+        private MessageHeader _header;
+        private IMessagePayload _payload;
+
+        public MessageHeader header
+        {
+            get { return _header; }
+            private set { }
+        }
+        public IMessagePayload payload
+        {
+            get { return _payload; }
+            private set { }
+        }
 
         public SBMessage()
         {
         }
 
[…]

### 2019-04-20 Smart-Bus/RequestPattern_2P_2S_2B.cs
Added a few more test cases, and made the existing ones more interesting
Also, changed some Constants values to make everything mesh better

@@ -9,8 +9,8 @@ namespace Smart_Bus
 
         private Request[] requests = 
         { 
-            new Request(5000, 6000, 0, 1), 
-            new Request(10000, 11000, 1, 0)
+            new Request(1, 5 * 1000, 15 * 1000, 1, 2), 
+            new Request(2, 10 * 1000, 20 * 1000, 2, 1)
         };
         
         private int currentRequest = 0;
@@ -20,7 +20,8 @@ namespace Smart_Bus
         public RequestPattern_2P_2S_2B()
         {
             // Sort the requests array in order of earliestServingTime on startup
-            // This is in-place selection sort so it's inefficient, but there won't be many requests so it's fine
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
             for (int i = 0; i < requests.Length - 1; i++)
             {
                 int minIdx = i;

### 2019-04-20 Smart-Bus/RequestPattern_2P_4S_1B.cs

@@ -4,22 +4,20 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_4P_4S_2B: IRequestPattern
+    class RequestPattern_2P_4S_1B: IRequestPattern
     {
 
         private Request[] requests = 
         { 
-            new Request(1, 5 * 1000, 15 * 1000, 1, 2),
-            new Request(2, 10 * 1000, 20 * 1000, 2, 1),
-            new Request(3, 5 * 1000, 15 * 1000, 3, 4),
-            new Request(4, 10 * 1000, 20 * 1000, 4, 3)
+            new Request(1, 5 * 1000, 15 * 1000, 1, 3), 
+            new Request(2, 5 * 1000, 15 * 1000, 2, 3)
         };
         
         private int currentRequest = 0;
         private int numStops = 4;
-        private int numBuses = 2;
+        private int numBuses = 1;
 
-        public RequestPattern_4P_4S_2B()
+        public RequestPattern_2P_4S_1B()
         {
             // Sort the requests array in order of earliestServingTime on startup
             // This is in-place selection sort so it's inefficient, but there 

### 2019-04-20 Smart-Bus/RequestPattern_4P_2S_2B.cs

@@ -8,11 +8,11 @@ namespace Smart_Bus
     {
 
         private Request[] requests = 
-        { 
-            new Request(1000, 2000, 0, 1), 
-            new Request(2000, 3000, 1, 0),
-            new Request(3000, 4000, 0, 1), 
-            new Request(4000, 5000, 1, 0) 
+        {
+            new Request(1, 1 * 1000, 11 * 1000, 1, 2), 
+            new Request(2, 2 * 1000, 12 * 1000, 2, 1),
+            new Request(3, 3 * 1000, 13 * 1000, 1, 2), 
+            new Request(4, 4 * 1000, 14 * 1000, 2, 1) 
         };
         
         private int currentRequest = 0;
@@ -22,7 +22,8 @@ namespace Smart_Bus
         public RequestPattern_4P_2S_2B()
         {
             // Sort the requests array in order of earliestServingTime on startup
-            // This is in-place selection sort so it's inefficient, but there won't be many requests so it's fine
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
             for (int i = 0; i < requests.Length - 1; i++)
             {
                 int minIdx = i;

### 2019-04-20 Smart-Bus/RequestPattern_8P_2S_2B.cs

@@ -9,14 +9,14 @@ namespace Smart_Bus
 
         private Request[] requests = 
         {
-            new Request(1000, 2000, 0, 1), 
-            new Request(2000, 3000, 1, 0),
-            new Request(3000, 4000, 0, 1), 
-            new Request(4000, 5000, 1, 0),
-            new Request(1000, 2000, 1, 0), 
-            new Request(2000, 3000, 0, 1),
-            new Request(3000, 4000, 1, 0), 
-            new Request(4000, 5000, 0, 1) 
+            new Request(1, 1 * 1000, 12 * 1000, 1, 2), 
+            new Request(2, 2 * 1000, 13 * 1000, 2 ,1),
+            new Request(3, 3 * 1000, 14 * 1000, 1, 2), 
+            new Request(4, 4 * 1000, 15 * 1000, 2, 1),
+            new Request(5, 1 * 1000, 11 * 1000, 2, 1), 
+            new Request(6, 2 * 1000, 12 * 1000, 1, 2),
+            new Request(7, 3 * 1000, 13 * 1000, 2, 1), 
+            new Request(8, 4 * 1000, 14 * 1000, 1, 2) 
         };
         
         private int currentRequest = 0;
@@ -26,7 +26,8 @@ namespace Smart_Bus
         public RequestPattern_8P_2S_2B()
         {
             // Sort the requests array in order of earliestServingTime on startup
-            // This is in-place selection sort so it's inefficient, but there won't be many requests so it's fine
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
             for (int i = 0; i < requests.Length - 1; i++)
             {
                 int minIdx = i;

### 2019-04-20 Smart-Bus/RequestPattern_8P_8S_4B.cs

@@ -4,22 +4,26 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_4P_4S_2B: IRequestPattern
+    class RequestPattern_8P_8S_4B: IRequestPattern
     {
 
         private Request[] requests = 
-        { 
-            new Request(1, 5 * 1000, 15 * 1000, 1, 2),
-            new Request(2, 10 * 1000, 20 * 1000, 2, 1),
-            new Request(3, 5 * 1000, 15 * 1000, 3, 4),
-            new Request(4, 10 * 1000, 20 * 1000, 4, 3)
+        {
+            new Request(1, 1 * 1000, 11 * 1000, 1, 5), 
+            new Request(2, 2 * 1000, 12 * 1000, 3 ,8),
+            new Request(3, 3 * 1000, 13 * 1000, 6, 2), 
+            new Request(4, 4 * 1000, 14 * 1000, 2, 1),
+            new Request(5, 5 * 1000, 15 * 1000, 7, 5), 
+            new Request(6, 6 * 1000, 16 * 1000, 1, 4),
+            new Request(7, 7 * 1000, 17 * 1000, 3, 2), 
+            new Request(8, 8 * 1000, 18 * 1000, 7, 8) 
         };
         
         private int currentRequest = 0;
-        private int numStops = 4;
-        private int numBuses = 2;
+        private int numStops = 8;
+        private int numBuses = 4;
 
-        public RequestPattern_4P_4S_2B()
+        public RequestPattern_8P_8S_4B()
         {
             // Sort the requests array in order of earliestServingTime on startup
             // This is in-place selection sort so it's inefficient, but there 

### 2019-04-20 Smart-Bus/Utilities/Constants.cs

@@ -5,9 +5,9 @@ namespace Smart_Bus
 {
     public class Constants
     {
-        // Every hop between bus stops is constant; for this demo, it takes 1 simulated minute
-        public static readonly int HOP_DURATION = 60000;
-        public static readonly int STOP_DURATION = 10000;
+        // Every hop between bus stops is constant; for this demo, it takes 10 simulated seconds
+        public static readonly int HOP_DURATION = 10 * 1000;
+        public static readonly int STOP_DURATION = 2 * 1000;
 
         // 1 is Real Time (i.e., one second of wall time per second of simulation time)
         // Suggested values are on the order of 100 (every 10 milliseconds of wall time is one second of simulation time)

### 2019-04-20 Report/paper.tex

@@
 % Sections
+\section{Assignment Description}
+Your final project report should include:
+\begin{itemize}
+	\item A write-up describing
+	\begin{itemize}
+		\item The design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API
+		\item Instructions and illustration of use, in terms of a README file and/or user guide,
+		\item How your implementation has been tested,
+		\item Performance of your implementation,
+		\item Assumptions or limitations of your design,
+		\item Any omissions or errors in your implementation, and
+		\item Any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)
+	\end{itemize}
+	\item Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.
+	\item Script of a session showing the program under test.
+\end{itemize}
 
 \section{Introduction}
-Your final project report should include:
-1. A write-up describing
-
-(a) the design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API
-
-(b) instructions and illustration of use, in terms of a README file and/or user guide,
-
-(c) how your implementation has been tested,
-
-(d) performance of your implementation,
-
-(e) assumptions or limitations of your design,
-
-(f) any omissions or errors in your implementation, and
-
-(g) any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)
-
-2. Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.
-
-3. Script of a session showing the program under test.
-
 Internet of Things (IoT) has been an innovative technology connecting heterogeneous devices to form a practical network for facilitation of human work.
@@
 Also, this paper aims to propose a distributed algorithm which efficiently solves the bus scheduling problem in the smart bus system so that the total travel time, sum of lateness over all pick-up and delivery locations, and sum of overtime over all buses can be minimized.
+
 \subsection{Smart Bus System}
@@
 We proposed low power Bus Service Access Points (BSAPs) with Wi-Fi and LPWAN to establish a mobile ad-hoc network with the ability to provide high speed transmission in short distance below 30 meters and low speed transmission in long distance in kilometers.
+
 In this system, each bus and bus stop are equipped with one BSAP.
@@
 
-Without attaching an additional LPWAN interface, a passenger will always use Wi-Fi radio to communicate with a BSAP on bus or bus stop.
+Without attatching an additional LPWAN interface, a passenger will always use Wi-Fi radio to communicate with a BSAP on bus or bus stop.
 On the other side, a BSAP can exploit the Wi-Fi interface with higher throughput to transmit message if the distance between two neighbor BSAPs is within an available Wi-Fi range.
@@
 Hence, to implement the system and meet the requirement from passengers, we need to solve the scheduling problem stated in the following sections.
+
 \subsection{Scheduling Problem}
-Let $p_i^+$ and $p_i^-$ respectively denote the pickup point and the delivery point of passenger i.
+Let $p_i^+$ and $p_i^-$ respectively denote the pickup point and the delivery point of passenger $i$.
 Also, we have earliest departure time $ED_i$ from point $p_i^+$, latest arrival time $LA_i$ to point $p_i^-$.
-The problem consists of a set $B = \{1, 2, …, m\}$ of m buses in the smart bus network with their current routes.
-For the route of bus k, it includes a combination of multiple pickup points and deliver points, which is denoted by $R_k = \{p_0, p_1, …, p_r\}$, where $p_i^+\in R_k$ if passenger i is matched to bus k and he has not been picked up and $p_i^-\in R_j$ if passenger i is matched to bus k and he has not reached his destination.
-The order of points in $R_k$ depends on the earliest departure time and the latest arrival time of matched passengers to bus k.
-If p is the number of matched passengers to bus k who have not been picked up and q is the number of matched passengers to bus k who have not reached their destinations.
-Thus, p must be equal to or greater than q.
-This is because there probably exist some passengers who have been picked up but not reached their destinations.
-For a bus k, it has limited capacity to serve passengers.
+The problem consists of a set $B = \{1, 2, \dots, m\}$ of $m$ buses in the smart bus network with their current routes.
+For the route of bus k, it includes a combination of multiple pickup points and deliver points, which is denoted by $R_k = \{p_0, p_1, \dots, p_r\}$, where $p_i^+\in R_k$ if passenger $i$ is matched to bus $k$ and he has not been picked up and $p_i^-\in R_j$ if passenger $i$ is matched to bus $k$ and he has not reached his destination.
+The order of points in $R_k$ depends on the earliest departure time and the latest arrival time of matched passengers to bus $k$.
+Suppose $p$ is the number of matched passengers to bus $k$ who have not been picked up and $q$ is the number of matched passengers to bus $k$ who have not reached their destinations.
+Then $p \geq q$ because there might exist some passengers who have been picked up but not reached their destinations (but there are no passengers which have reached their destinations that have not yet been picked up).
+For a bus $k$, it has limited capacity to serve passengers.
 Assume all buses in the network have the same capacity.
-Let $c_{k,v}$ be the number of seat available in bus k when arriving location v.
-$c_{k,v}$ decreases by 1 after serving location v which belongs a pickup location.
+Let $c_{k,v}$ be the number of seats available in bus $k$ when arriving location $v$.
+$c_{k,v}$ decreases by 1 after serving location $v$ which is a pickup location.
 Otherwise, $c_{k,v}$ increase by 1 after serving a delivery location.
-A bus k cannot serve any passengers at a pickup location v if $c_{k,v}$ is 0.
+A bus $k$ cannot serve any passengers at a pickup location $v$ if $c_{k,v} = 0$.
 
-Moreover, let $t_{a,b}$ be the direct travel time between points a and b.
-For each service location v (pickup or delivery point), we compute time windows of this service location $[e_v, l_v]$, which denotes the earliest and latest served time.
-For example, for a request i with pickup point $p_i^+$ and delivery point $p_i^-$, we can calculate the time window of $p_i^+$, $[ED_i, LA_i – t_{p_i^+,p_i^-}]$ and the time window of $c_i^-$, $[ED_i + t_{p_i^+,p_i^-}, LA_i]$.
-In the system, each bus starts and ends its route at the bus terminus (location 0).
-Let $ts_k$ and $te_k$ denote start time and end time for bus k.
+Moreover, let $t_{a,b}$ be the direct travel time between points $a$ and $b$.
+For each service location $v$ (either a pickup or delivery point), we compute time windows of this service location $[e_v, l_v]$, which denotes the earliest and latest served time.
+For example, for a request $i$ with pickup point $p_i^+$ and delivery point $p_i^-$, we can calculate the time window of $p_i^+$, $[ED_i, LA_i – t_{p_i^+,p_i^-}]$ and the time window of $c_i^-$, $[ED_i + t_{p_i^+,p_i^-}, LA_i]$.
+In the system, each bus starts and ends its route at the \emph{bus terminus} (location 0).
+Let $ts_k$ and $te_k$ denote start time and end time for bus $k$.
 There is also a time window at the terminus, where $e_0$ and $l_0$ are the earliest start time and latest end time of each route.
 
-Let $t_v$ denote the serving time at point v by the matched bus.
+Let $t_v$ denote the serving time at point $v$ by the matched bus.
 It denotes the exact pick or delivery times for passengers.
-If v’ is the predecessor of v in a route, the arrival time of the bus k at v is $t_v = max(t_{v’}, e_{v’}) + t_{v’, v}$; otherwise $t_v$ = $ts_k$ + $t_{0, v}$.
-Since the requests from passengers are dynamic and independent, the problem is to find a matched bus for a newly added passenger in real time while the system receives a request from him and to readjust the route of the matched bus in order to minimize total travel time of buses, sum of lateness over all pick-up and delivery locations, and sum of overtime over all buses.
-Thus, we can define the problem as the statement provided below:
+If $v’$ is the predecessor of $v$ in a route, the arrival time of the bus $k$ at $v$ is $t_v = max(t_{v’}, e_{v’}) + t_{v’, v}$; otherwise $t_v = ts_k$ + $t_{0, v}$.
 
-Given a set $B = \{1, 2, …, m\}$ of m buses on the route.
-Each bus k has the current route $R_k = \{p_0, p_1, …\}$.
-Whenever receiving a request from passenger i with the parameters $p_i^+$, $p_i^-$, $ED_i$, and $LA_i$, we compute the matched bus and insert the pickup point $p_i^+$ and delivery point $p_i^-$ to the route $R_j$ of matched bus j according to the time windows of service location $[e_v, l_v]$.
+Since the requests from passengers are dynamic and independent, the problem is to find a matched bus for a newly added passenger in real time while the system receives a request from him and to adjust the route of the matched bus in order to minimize the total travel time of buses, the sum of ``lateness'' over all pick-up and delivery locations, and the sum of overtime over all buses.
+Thus, we can define the problem as the statement provided below.
+
+Given a set $B = \{1, 2, \dots, m\}$ of m buses on the route.
+Each bus $k$ has the current route $R_k = \{p_0, p_1, \dots\}$.
+Whenever receiving a request from passenger $i$ with the parameters $p_i^+$, $p_i^-$, $ED_i$, and $LA_i$, we compute the matched bus and insert the pickup point $p_i^+$ and delivery point $p_i^-$ to the route $R_j$ of matched bus $j$ according to the time windows of service location $[e_v, l_v]$.
 The goal is to minimize the objective function:
@@
 
-$T_k$ denotes the total travel time of bus k. The weights $\alpha$ and $\beta$ define the relative importance of the different components.
+$T_k$ denotes the total travel time of bus $k$. The weights $\alpha$ and $\beta$ define the relative importance of the different components.
 
@@
 Since the goal is to minimize the objective function, whenever assigning requests from passenger, a serving bus stop needs to compare a metric of buses to select the best bus leading to the minimized result of objective function.
-Thus, we define a metric, route flexibility, to evaluate the flexibility to accommodate a new request into the current route.
-Let $f_{k,v}$ denote the flexible time of  bus k at location v, which is defined by $l_v – t_v$.
-That is to say, if the arrival time tv is much smaller than the latest served time $l_v$, then the bus has the higher flexibility to accept more requests.
+Thus, we define a metric, \emph{route flexibility}, to evaluate the flexibility to accommodate a new request into the current route.
+Let $f_{k,v}$ denote the flexible time of bus $k$ at location $v$, which is defined by $l_v – t_v$.
+That is to say, if the arrival time $t_v$ is much smaller than the latest served time $l_v$, then the bus has the higher flexibility to accept more requests.
 Hence, to calculate the route flexibility, we use $F_k$ to denote the accumulated flexible time of service locations in $R_k$.
@@
 $l_0 - te_k$, the flexible time at terminus, decreases or stays the same whenever a new request is added to $R_k$.
-Note that $\sum_{k\in B}{F_k}$ is inversely proportional to objective function.
+Note that $\sum_{k\in B}{F_k}$ (i.e., the total flexibility) is inversely proportional to objective function.
 Hence, objective function can be minimized if the total route flexibility is maximized during request assigning for each bus stop.
+
 \subsection{Route Information Sharing}
 When assigning requests, the serving bus stop must know the current route information of buses and their current capacity.
-For example, if bus k picked up a passenger at location v, then the number of service location in $R_k$ decreased and the capacity $c_k$ decreased as well.
-At that time, bus k should update the information to bus stops.
+For example, if bus $k$ picked up a passenger at location $v$, then the number of service location in $R_k$ decreased and the capacity $c_k$ decreased as well.
+At that time, bus $k$ should update the information to bus stops.
+
 \subsection{Request Assignment Algorithm}
 With the route information of buses, a bus stop is able to compare the route flexibility of different buses after inserting a request to their routes.
-However, when receiving a new request, instead of immediately assigning it to a bus, the serving bus stop will wait for a certain to determine which request should be served first and which bus is the best one to serve the request.
+However, when receiving a new request, instead of immediately assigning it to a bus, the serving bus stop will wait for a certain amount of time to determine which request should be served first and which bus is the best one to serve the request.
 This is because all requests are dynamically launched by passengers, bus stops do not know requests in advance until receiving them.
 To maximize the total flexibility as possible, bus stops should serve requests according to the urgency rather than the receiving order since we know an urgent request can harm the route flexibility if it is not immediately assigned to a bus.
-On the other hand, the request, with larger latest arrival time, can be reasonably delayed for a certain time because buses may need to reserve space for the potentially future urgent request.
+On the other hand, the request, with larger latest arrival time, can be reasonably delayed for a certain time because buses may need to reserve space for a potentially urgent future request.
 
-Let $\delta$ denote the urgent threshold.
-For a request i, if $LA_i - \delta$ is smaller than the current time, we can say it is an urgent request.
+Let $\delta$ denote the urgency threshold.
+For a request $i$, if $LA_i - \delta$ is smaller than the current time, we can say it is an urgent request.
 For assigning urgent requests, a serving bus stop assign the request to the bus with maximal route flexibility after inserting the request.

### 2019-04-21 Smart-Bus/Utilities/BusStop.cs
Update BusStop.cs

@@ -362,7 +362,7 @@ namespace Smart_Bus
             {
                 Request_v[] routeInfo_tmp_o = Append_route(null, new_origin);
                 Request_v[] routeInfo_tmp_o_d = Append_route(routeInfo_tmp_o, new_destination);
-                bus_list[bus_index].routeInfo = routeInfo_tmp_o_d;
+                bus_list[bus_index].pending_routeInfo = routeInfo_tmp_o_d;
                 return;
             }
             else
@@ -390,7 +390,7 @@ namespace Smart_Bus
                         if (flex > max_flex)
                         {
                             max_flex = flex;
-                            bus_list[bus_index].routeInfo = routeInfo_tmp_o_d;
+                            bus_list[bus_index].pending_routeInfo = routeInfo_tmp_o_d;
                         }
                     }
                 }
@@ -411,7 +411,7 @@ namespace Smart_Bus
                                 if (flex > max_flex)
                                 {
                                     max_flex = flex;
-                                    bus_list[bus_index].routeInfo = routeInfo_tmp_o_d;
+                                    bus_list[bus_index].pending_routeInfo = routeInfo_tmp_o_d;
                                 }
                             }
                         }

### 2019-04-21 Bus-Stop/BusStopDriver.cs
Added Guard to BusDriver messagehandling
BusDriver only deals with messages that are meant for that bus

@@ -122,7 +122,7 @@ namespace Smart_Bus
                     {
                         //Update the route info
                         Bus_info element = new Bus_info();
-                        element.busId = message.header.origin.endptId;
+                        element.busId = message.header.source.endptId;
 
                         Route payload = (Route)message.payload;
                         element.NumServed = payload.NumServed;

### 2019-04-21 Bus/BusDriver.cs

@@ -62,66 +62,75 @@ namespace Smart_Bus
             Debug.Print("Received message: " + msgString);
             SBMessage.MessageType msgType = message.header.type;
             Bus bus = BusDriver.getInstance().myBus;
-            switch (msgType)
+            
+            // Only handle the message if it is meant for us
+            SBMessage.MessageEndpoint msgDest = message.header.destination;
+            if (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BROADCAST ||
+                (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BUS &&
+                    msgDest.endptId == bus.id))
             {
-                case SBMessage.MessageType.START_SIMULATION:
-                    {
-                        BusDriver.SimStart = ((PayloadSimStart)message.payload).date;
-                        Utilities.SimStart = BusDriver.SimStart;
-                        break;
-                    }
-                case SBMessage.MessageType.ROUTE_INFO_REQUEST:
-                    {
-                        int stopId = message.header.source.endptId;
-
-                        // Only reply if we're "nearby"
-                        //  *Note: IsNearbyStop simply returns true for this project;
-                        //  this is a necessary simplification due to the deadline.
-                        // A real system would reply only if the stop is in our immediate
-                        //  future along the route; the stops themselves would employ BFS
-                        //  to find all buses. See the implementation for details.
-                        if (bus.IsNearbyStop(stopId))
+                switch (msgType)
+                {
+                    case SBMessage.MessageType.START_SIMULATION:
                         {
-                            // A bus stop is asking for route information
-                            // from "nearby" buses, and we're one of them
+                            PayloadSimStart startPayload = (PayloadSimStart)message.payload;
+                            BusDriver.SimStart = startPayload.date;
+                            Utilities.SimStart = BusDriver.SimStart;
+                            break;
+                        }
+                    case SBMessage.MessageType.ROUTE_INFO_REQUEST:
+                        {
+                            int stopId = message.header.source.endptId;
 
-                            IMessagePayload replyPayload = bus.route;
+                            // Only reply if we're "nearby"
+                            //  *Note: IsNearbyStop simply returns true for this project;
+                            //  this is a necessary simplification due to the deadline.
+                            // A real system would reply only if the stop is in our immediate
+                            //  future along the route; the stops themselves would employ BFS
+                            //  to find all buses. See the implementation for details.
+                            if (bus.IsNearbyStop(stopId))
+                            {
[…]

### 2019-04-21 Smart-Bus/Utilities/Route.cs

@@ -119,6 +119,10 @@ namespace Smart_Bus
 
         public String BuildPayload()
         {
+            if (this.importantStops.Count == 0)
+            {
+                return " ";
+            }
             StringBuilder payload = new StringBuilder();
             int numServed = this.NumServed;
             for (int i = 0; i < this.importantStops.Count; i++)

### 2019-04-21 Smart-Bus/Utilities/SBMessage.cs

@@ -103,6 +103,7 @@ namespace Smart_Bus
 
         public SBMessage(string msgString)
         {
+            msgString = msgString.TrimEnd();
             string[] components = msgString.Split();
 
             int mTypeInt = int.Parse(components[0]);

### 2019-04-21 Smart-Bus/Utilities/Utilities.cs

@@ -31,8 +31,9 @@ namespace Smart_Bus
             //Debug.Print("Milliseconds btwn " + SimStart.ToString(Constants.DATE_TIME_FORMAT) + " to " + DateTime.Now.ToString(Constants.DATE_TIME_FORMAT) + ": " + ElapsedMillis());
             //Thread.Sleep(Timeout.Infinite);
 
-            SBMessage message = new SBMessage("11 1 -1 2 1 1 1000 15000 1 2 ");
-            Debug.Print(message.header.type.ToString());
+            SBMessage message = new SBMessage("30 0 0 2 1 ");
+            Route r = (Route)message.payload;
+            Debug.Print("<" + r.BuildPayload() + ">");
         }
 
         public static byte[] StringToByteArray(String s)

### 2019-04-21 Bus-Stop/BusStopDriver.cs
Update BusStopDriver.cs

@@ -64,161 +64,170 @@ namespace Smart_Bus
             SBMessage.MessageType msgType = message.header.type;
             BusStop stop = BusStopDriver.getInstance().myBusStop;
 
-            switch (msgType)
+
+            // Only handle the message if it is meant for the stop
+            SBMessage.MessageEndpoint msgDest = message.header.destination;
+            if (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BROADCAST ||
+                (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BUS_STOP &&
+                    msgDest.endptId == instance.myBusStop.id))
             {
-                case SBMessage.MessageType.START_SIMULATION:
-                    {
-                        BusStopDriver.SimStart = ((PayloadSimStart)message.payload).date;
-                        Utilities.SimStart = BusStopDriver.SimStart;
-                        instance.myBusStop.SimStart = BusStopDriver.SimStart;
 
-                        //here we know the number of buses in the network, 
-                        //so we can know how many messages of ROUTE_INFO_RESPONSE the stop has to wait after sending ROUTE_INFO_REQUEST
-                        PayloadSimStart payload = (PayloadSimStart)message.payload;
-                        instance.myBusStop.numBuses = payload.numBuses;
-
-                        break;
-                    }
-                case SBMessage.MessageType.SEND_PASSENGER_REQUEST:
-                    {
-                        //Send ROUTE_INFO_REQUEST to buses while receiving a request but the stop does not have route info
-                        SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS_STOP, instance.myBusStop.id);
-                        SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint();
-                        SBMessage m = new SBMessage(SBMessage.MessageType.ROUTE_INFO_REQUEST, origin, destination, new PayloadSimpleString());
-                        m.Broadcast(BusStopDriver.getInstance().NetPort);
-
-                        switch (instance.myBusStop.stop_state)
+                switch (msgType)
+                {
+                    case SBMessage.MessageType.START_SIMULATION:
                         {
-                            case BusStop_State.REQUEST_NULL:
-                            case BusStop_State.REQUEST_READY_TO_BE_ASSIGNED:
[…]

### 2019-04-21 Bus-Stop/BusStopDriver.cs
Bus acknowledges new requests based on current capacity

@@ -130,7 +130,7 @@ namespace Smart_Bus
                         {
                             //Update the route info
                             Bus_info element = new Bus_info();
-                            element.busId = message.header.origin.endptId;
+                            element.busId = message.header.source.endptId;
 
                             Route payload = (Route)message.payload;
                             element.NumServed = payload.NumServed;

### 2019-04-21 Bus/BusDriver.cs

@@ -27,6 +27,7 @@ namespace Smart_Bus
 
         private static UInt16 appId;
         private static DateTime SimStart;
+        private SBMessage.MessageEndpoint messageSource;
 
         private BusDriver()
         {
@@ -96,7 +97,7 @@ namespace Smart_Bus
                                 IMessagePayload replyPayload = bus.route;
                                 SBMessage reply = new SBMessage(
                                     SBMessage.MessageType.ROUTE_INFO_RESPONSE,
-                                    message.header.destination,
+                                    BusDriver.getInstance().messageSource,
                                     message.header.source,
                                     replyPayload);
                                 reply.Broadcast(BusDriver.getInstance().NetPort);
@@ -111,7 +112,7 @@ namespace Smart_Bus
                             // I believe the only way we this won't be true here is if
                             //  another stop has changed our route since this stop last
                             //  received info about our route.
-                            if (bus.route.IsRequestSubsetOf(newRoute))
+                            if (bus.HasCapacityNow())
                             {
                                 // If this is an acceptable route to change to, 
                                 //  then update our route
@@ -121,10 +122,12 @@ namespace Smart_Bus
 
                             IMessagePayload replyPayload = new PayloadRouteChangeAckResponse(confirm, bus.route);
 
+                            Debug.Print("Acknowledging ROUTE_CHANGE_REQUEST with " + confirm.ToString());
+
                             // Notify the stop one way or the other about whether we accepted the new route
                             SBMessage reply = new SBMessage(
                                 SBMessage.MessageType.ROUTE_CHANGE_ACK,
-                                message.header.destination,
+                                BusDriver.getInstance().messageSource,
                                 message.header.source,
                                 replyPayload);
                             reply.Broadcast(BusDriver.getInstance().NetPort);
@@ -143,6 +146,7 @@ namespace Smart_Bus
             Debug.Print("Successfully got ID from the Hub: " + appId.ToString());
 
             instance.myBus = new Bus(appId);
+            instance.messageSource = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS, appId);
 
             Thread.Sleep(Timeout.Infinite);
         }

### 2019-04-21 Smart-Bus/RequestDriver.cs

@@ -72,7 +72,7 @@ namespace Smart_Bus
         public static void Main()
         {
             RequestDriver driver = RequestDriver.getInstance();
-            driver.pattern = new RequestPattern_1P_2S_1B();
+            driver.pattern = new RequestPattern_2P_2S_1B();
             driver.NetPort.Init();
             Thread.Sleep(100);
             appId = driver.NetPort.GetID();

### 2019-04-21 Smart-Bus/RequestPattern_2P_2S_1B.cs

@@ -4,20 +4,20 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_2P_2S_2B: IRequestPattern
+    class RequestPattern_2P_2S_1B: IRequestPattern
     {
 
         private Request[] requests = 
         { 
-            new Request(1, 5 * 1000, 15 * 1000, 1, 2), 
-            new Request(2, 10 * 1000, 20 * 1000, 2, 1)
+            new Request(1, 5 * 1000, 25 * 1000, 1, 2), 
+            new Request(2, 10 * 1000, 30 * 1000, 1, 2)
         };
         
         private int currentRequest = 0;
         private int numStops = 2;
-        private int numBuses = 2;
+        private int numBuses = 1;
 
-        public RequestPattern_2P_2S_2B()
+        public RequestPattern_2P_2S_1B()
         {
             // Sort the requests array in order of earliestServingTime on startup
             // This is in-place selection sort so it's inefficient, but there 

### 2019-04-21 Smart-Bus/Utilities/Bus.cs

@@ -38,5 +38,10 @@ namespace Smart_Bus
             //return 0 <= stopsUntilEncounter && stopsUntilEncounter < NearbyThreshold;
             return true;
         }
+
+        public bool HasCapacityNow()
+        {
+            return this.route.CurrentCapacity() > 0;
+        }
     }
 }

### 2019-04-21 Smart-Bus/Utilities/BusStop.cs

@@ -583,6 +583,7 @@ namespace Smart_Bus
             if (this.request_list.Length == 1 && index == 0)
             {
                 request_list = null;
+                return;
             }
 
             Request[] new_list = new Request[this.request_list.Length - 1];

### 2019-04-21 Smart-Bus/Utilities/Request.cs

@@ -142,7 +142,7 @@ namespace Smart_Bus
             payload.Append(this.earliestServingTime.ToString() + " ");
             payload.Append(this.latestServingTime.ToString() + " ");
             payload.Append(this.is_origin ? "1 " : "0 ");
-            payload.Append(this.stop.id);
+            payload.Append(this.stop.id.ToString() + " ");
             payload.Append(this.served ? "1 " : "0 ");
             return payload.ToString();
         }

### 2019-04-21 Smart-Bus/Utilities/Route.cs

@@ -119,10 +119,6 @@ namespace Smart_Bus
 
         public String BuildPayload()
         {
-            if (this.importantStops.Count == 0)
-            {
-                return " ";
-            }
             StringBuilder payload = new StringBuilder();
             int numServed = this.NumServed;
             for (int i = 0; i < this.importantStops.Count; i++)
@@ -135,6 +131,26 @@ namespace Smart_Bus
                 payload.Append(stop.BuildPayload());
             }
             return payload.ToString();
+        }
+
+        internal int CurrentCapacity()
+        {
+            int elapsedSimulationMillis = Utilities.ElapsedSimulationMillis();
+            int currCap = Bus.CAPACITY;
+            int numServed = this.NumServed;
+            for (int i = 0; i < numServed; i++)
+            {
+                Request_v stop = this[i];
+                if (stop.is_origin)
+                {
+                    currCap--;
+                }
+                else
+                {
+                    currCap++;
+                }
+            }
+            return currCap;
         }
     }
 }

### 2019-04-21 Smart-Bus/Utilities/SBMessage.cs

@@ -158,6 +158,7 @@ namespace Smart_Bus
         {
             Debug.Print(DateTime.Now.ToString("HH:mm:ss.fff") + ": Sending message " + this.ToString());
             byte[] msgBytes = Utilities.StringToByteArray(this.ToString());
+            Thread.Sleep(100);
             NetPort.Broadcast(msgBytes, msgBytes.Length);
         }
     }

### 2019-04-21 Smart-Bus/Utilities/Constants.cs
Update Constants.cs

@@ -5,9 +5,9 @@ namespace Smart_Bus
 {
     public class Constants
     {
-        // Every hop between bus stops is constant; for this demo, it takes 10 simulated seconds
-        public static readonly int HOP_DURATION = 10 * 1000;
-        public static readonly int STOP_DURATION = 2 * 1000;
+        // Every hop between bus stops is constant; for this demo, it takes 3 simulated minutes
+        public static readonly int HOP_DURATION = 3 * 60 * 1000;
+        public static readonly int STOP_DURATION = 30 * 1000;
 
         // 1 is Real Time (i.e., one second of wall time per second of simulation time)
         // Suggested values are on the order of 100 (every 10 milliseconds of wall time is one second of simulation time)

### 2019-04-21 Smart-Bus/RequestPattern_1P_2S_1B.cs
Request Patterns updated with one-stop departures
Due to (as far as we can tell) an error in the emulator, we were forced to limit the number of bus stop processes to 1; thus, all requests must be sourced from the same stop.

@@ -9,7 +9,7 @@ namespace Smart_Bus
 
         private Request[] requests = 
         { 
-            new Request(1, 1 * 1000, 15 * 1000, 1, 2)
+            new Request(1, 1 * 60 * 1000, 15 * 60 * 1000, 1, 2)
         };
         
         private int currentRequest = 0;

### 2019-04-21 Smart-Bus/RequestPattern_2P_2S_1B.cs

@@ -9,8 +9,8 @@ namespace Smart_Bus
 
         private Request[] requests = 
         { 
-            new Request(1, 5 * 1000, 25 * 1000, 1, 2), 
-            new Request(2, 10 * 1000, 30 * 1000, 1, 2)
+            new Request(1, 1 * 60 * 1000, 25 * 60 * 1000, 1, 2), 
+            new Request(2, 1 * 60 * 1000, 30 * 60 * 1000, 1, 2)
         };
         
         private int currentRequest = 0;

### 2019-04-21 Smart-Bus/RequestPattern_2P_4S_1B.cs

@@ -9,8 +9,8 @@ namespace Smart_Bus
 
         private Request[] requests = 
         { 
-            new Request(1, 5 * 1000, 15 * 1000, 1, 3), 
-            new Request(2, 5 * 1000, 15 * 1000, 2, 3)
+            new Request(1, 5 * 60 * 1000, 15 * 60 * 1000, 1, 3), 
+            new Request(2, 5 * 60 * 1000, 15 * 60 * 1000, 1, 2)
         };
         
         private int currentRequest = 0;

### 2019-04-21 Smart-Bus/RequestPattern_4P_2S_2B.cs

@@ -9,10 +9,10 @@ namespace Smart_Bus
 
         private Request[] requests = 
         {
-            new Request(1, 1 * 1000, 11 * 1000, 1, 2), 
-            new Request(2, 2 * 1000, 12 * 1000, 2, 1),
-            new Request(3, 3 * 1000, 13 * 1000, 1, 2), 
-            new Request(4, 4 * 1000, 14 * 1000, 2, 1) 
+            new Request(1, 1 * 60 * 1000, 11 * 60 * 1000, 1, 2), 
+            new Request(2, 2 * 60 * 1000, 12 * 60 * 1000, 1, 1),
+            new Request(3, 3 * 60 * 1000, 13 * 60 * 1000, 1, 2), 
+            new Request(4, 4 * 60 * 1000, 14 * 60 * 1000, 1, 1) 
         };
         
         private int currentRequest = 0;

### 2019-04-21 Smart-Bus/RequestPattern_4P_4S_2B.cs

@@ -9,10 +9,10 @@ namespace Smart_Bus
 
         private Request[] requests = 
         { 
-            new Request(1, 5 * 1000, 15 * 1000, 1, 2),
-            new Request(2, 10 * 1000, 20 * 1000, 2, 1),
-            new Request(3, 5 * 1000, 15 * 1000, 3, 4),
-            new Request(4, 10 * 1000, 20 * 1000, 4, 3)
+            new Request(1, 5 * 60 * 1000, 15 * 60 * 1000, 1, 2),
+            new Request(2, 10 * 60 * 1000, 20 * 60 * 1000, 1, 3),
+            new Request(3, 5 * 60 * 1000, 15 * 60 * 1000, 1, 4),
+            new Request(4, 10 * 60 * 1000, 20 * 60 * 1000, 1, 2)
         };
         
         private int currentRequest = 0;

### 2019-04-21 Smart-Bus/RequestPattern_8P_2S_2B.cs

@@ -9,14 +9,14 @@ namespace Smart_Bus
 
         private Request[] requests = 
         {
-            new Request(1, 1 * 1000, 12 * 1000, 1, 2), 
-            new Request(2, 2 * 1000, 13 * 1000, 2 ,1),
-            new Request(3, 3 * 1000, 14 * 1000, 1, 2), 
-            new Request(4, 4 * 1000, 15 * 1000, 2, 1),
-            new Request(5, 1 * 1000, 11 * 1000, 2, 1), 
-            new Request(6, 2 * 1000, 12 * 1000, 1, 2),
-            new Request(7, 3 * 1000, 13 * 1000, 2, 1), 
-            new Request(8, 4 * 1000, 14 * 1000, 1, 2) 
+            new Request(1, 1 * 60 * 1000, 12 * 60 * 1000, 1, 2), 
+            new Request(2, 2 * 60 * 1000, 13 * 60 * 1000, 1 ,2),
+            new Request(3, 3 * 60 * 1000, 14 * 60 * 1000, 1, 2), 
+            new Request(4, 4 * 60 * 1000, 15 * 60 * 1000, 1, 2),
+            new Request(5, 1 * 60 * 1000, 11 * 60 * 1000, 1, 2), 
+            new Request(6, 2 * 60 * 1000, 12 * 60 * 1000, 1, 2),
+            new Request(7, 3 * 60 * 1000, 13 * 60 * 1000, 1, 2), 
+            new Request(8, 4 * 60 * 1000, 14 * 60 * 1000, 1, 2) 
         };
         
         private int currentRequest = 0;

### 2019-04-21 Smart-Bus/RequestPattern_8P_8S_4B.cs

@@ -10,13 +10,13 @@ namespace Smart_Bus
         private Request[] requests = 
         {
             new Request(1, 1 * 1000, 11 * 1000, 1, 5), 
-            new Request(2, 2 * 1000, 12 * 1000, 3 ,8),
-            new Request(3, 3 * 1000, 13 * 1000, 6, 2), 
-            new Request(4, 4 * 1000, 14 * 1000, 2, 1),
-            new Request(5, 5 * 1000, 15 * 1000, 7, 5), 
+            new Request(2, 2 * 1000, 12 * 1000, 1 ,8),
+            new Request(3, 3 * 1000, 13 * 1000, 1, 2), 
+            new Request(4, 4 * 1000, 14 * 1000, 1, 6),
+            new Request(5, 5 * 1000, 15 * 1000, 1, 5), 
             new Request(6, 6 * 1000, 16 * 1000, 1, 4),
-            new Request(7, 7 * 1000, 17 * 1000, 3, 2), 
-            new Request(8, 8 * 1000, 18 * 1000, 7, 8) 
+            new Request(7, 7 * 1000, 17 * 1000, 1, 2), 
+            new Request(8, 8 * 1000, 18 * 1000, 1, 7) 
         };
         
         private int currentRequest = 0;

### 2019-04-21 Smart-Bus/RequestDriver.cs
Added a debug statement to the SBMessage constructor
Also added more emulator logs, and changed the Request Pattern in RequestDriver, and changed Constants.TIME_MULT

@@ -72,7 +72,7 @@ namespace Smart_Bus
         public static void Main()
         {
             RequestDriver driver = RequestDriver.getInstance();
-            driver.pattern = new RequestPattern_2P_2S_1B();
+            driver.pattern = new RequestPattern_1P_2S_1B();
             driver.NetPort.Init();
             Thread.Sleep(100);
             appId = driver.NetPort.GetID();

### 2019-04-21 Smart-Bus/Utilities/Constants.cs

@@ -11,7 +11,7 @@ namespace Smart_Bus
 
         // 1 is Real Time (i.e., one second of wall time per second of simulation time)
         // Suggested values are on the order of 100 (every 10 milliseconds of wall time is one second of simulation time)
-        public static readonly int TIME_MULTIPLIER = 1;
+        public static readonly int TIME_MULTIPLIER = 100;
 
         // DateTime format string for all messages
         public static string DATE_TIME_FORMAT = "yyyy'-'MM'-'dd'T'H':'mm':'ss.fff";

### 2019-04-21 Smart-Bus/Utilities/SBMessage.cs

@@ -103,8 +103,8 @@ namespace Smart_Bus
 
         public SBMessage(string msgString)
         {
-            msgString = msgString.TrimEnd();
-            string[] components = msgString.Split();
+            Debug.Print("Received Message: " + msgString);
+            string[] components = msgString.TrimEnd().Split();
 
             int mTypeInt = int.Parse(components[0]);
             MessageType msgType = (MessageType)int.Parse(components[0]);

### 2019-04-22 Report/paper.tex
Merge branch 'master' of https://github.com/alanweide/Smart-Bus

@@
 \subsection{Limitations, Challenges, and Omissions}
+\subsubsection{Network Topology}
+In an effort to dramatically simplify many of the calculations involved in this algorithm, this version of the system assumes that all stops are arranged in a line, and that buses can travel directly only between neighboring stops.
+The algorithm as specified, of course, can handle arbitrary network topology, but our simplified implementation cannot.
+However, there are artifacts in the source code which were placed with the express purpose of ensuring this system remains extensible, and so could be adapted to handle arbitarily complex network topologies.
+
 \subsubsection{Passenger Behavior}
@@
 The efficacy of this (admittedly complicated) distributed algorithm versus a naive, static scheduling approach was evaluated.
-The static scheduling approach is similar to that employed by real public bus systems in the world: there are $n$ buses, each with a predetermined route $R$ through a number of stops.
+The static scheduling approach is similar to that employed by real public bus systems in the world: there are $N$ buses, each with a predetermined route $R$ through a number of stops.
 
@@
 
-\subsubsection{Specification of Static Approach}
+\subsubsection{Request Patterns}
+A variety of request patterns were used for evaluation. The scale of these patterns range from two passengers to ???, from two bus stops to ???, and from two buses to ???.
 
-\subsubsection{Request Patterns}
-A variety of request patterns were used for evaluation. The scales of these patterns range from two passengers to ???, from three bus stops to ???, and from two buses to ???.
+\subsubsection{Specification and Evaluation of Static Approach}
+The control for this experiment was a static, ``dummy'' approach (which we call the \emph{Traversal} approach) in which $N$ buses traverse the line of stops from one end to the other, and then back again.
+Its efficacy was evaluated from a purely theoretical standpoint; there is no implementation of the static algorithm.
+For each Request Pattern on which the Smart-Bus algorithm was tested, the minimum number of buses required by the Traversal approach to serve those requests on time (or, with minimal lateness) was computed.
+The results are summarized in Table~\ref{tbl:traversal} below.
+
+The method for computing the values in the table is quite simple, given the assumptions made about the toplogy and travel time between stops.
+For a traversing bus $B_i$, its route $R = \langle 0, 1, 2, \dots, N-1, N, N-1, N-2, \dots, 1, 0, 1, 2, \dots \rangle$, repeated until the total travel time is greater than its operating window: $T_{B_i} > (l_0 - e_0)$.
+Thus, given a system with hop duration $H$ and stop duration $S$, the number of stops along a bus's route is $B_S = \frac{l_0 - e_0}{H + S} + 1$ and the number of traversals made by a bus is $B_T = \frac{B_S}{N}$, and the time it takes for a traversal in a system with $N$ stops is $T_N = N (H + S) + S$.
+
+Since a bus will never change its route, it is trivial to predict exactly where it will be along its route at a given point in time.
+This information can then be used to determine, at the time a request is made, when the next bus to that stop will arrive and how long it will take to arrive at the request's destination.
+If any request cannot be served in time, an extra bus must be placed in the network.
+By repeatedly applying these calculations, we compute the minimum number of buses required to serve all requests in time.
+
+\setlength{\tabcolsep}{1em}
+\begin{table}[htbp]
+\centering
+\caption{Evaluating the Traversal Approach.}
+\begin{tabular}{c c c}
+Request Pattern & Min \# of Buses & Total Lateness \\ \hline
+2P\_2B\_2S & ? & ?\\
+4P\_2B\_2S & ? & ?\\
+6P\_4B\_4S & ? & ?\\
+8P\_4B\_8S & ? & ?\\
+\hline
+\end{tabular}
+\label{tbl:traversal}
+\end{table}
 

### 2019-04-22 Bus-Stop/BusStopDriver.cs

@@ -6,6 +6,8 @@ using Microsoft.SPOT.Hardware;
 using Microsoft.SPOT.Messaging;
 using System.IO.Ports;
 using Samraksh.SPOT.Emulator.Network;
+using System.Collections;
+
 
 namespace Smart_Bus
 {
@@ -43,6 +45,16 @@ namespace Smart_Bus
             return BusStopDriver.instance;
         }
 
+        private static void SendRouteChangeRequest(int bus_index)
+        {
+            SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS_STOP, instance.myBusStop.id);
+            SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS, instance.myBusStop.bus_list[bus_index].busId);
+            IMessagePayload payload = new Route(instance.myBusStop.bus_list[bus_index].routeInfo);
+            SBMessage message = new SBMessage(SBMessage.MessageType.ROUTE_CHANGE_REQUEST, origin, destination, payload);
+            message.Broadcast(BusStopDriver.getInstance().NetPort);
+
+        }
+
         public static void ReadNetworkPkt(byte[] msg, int size)
         {
 
@@ -52,52 +64,170 @@ namespace Smart_Bus
             SBMessage.MessageType msgType = message.header.type;
             BusStop stop = BusStopDriver.getInstance().myBusStop;
 
-            switch (msgType)
-            {
-                case SBMessage.MessageType.START_SIMULATION:
-                    {
-                        BusStopDriver.SimStart = ((PayloadDateTime)message.payload).date;
-                        Utilities.SimStart = BusStopDriver.SimStart;
-                        instance.myBusStop.SimStart = BusStopDriver.SimStart;
-                        break;
-                    }
-                case SBMessage.MessageType.SEND_PASSENGER_REQUEST:
-                    {
-                        Request new_request = (Request)message.payload;
 
-                        //If the bus stop does not have any busInfo, it has to send ROUTE_INFO_REQUEST first
-                        if (instance.myBusStop.busInfo_list == null)
+            // Only handle the message if it is meant for the stop
+            SBMessage.MessageEndpoint msgDest = message.header.destination;
+            if (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BROADCAST ||
+                (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BUS_STOP &&
[…]

### 2019-04-22 Bus/BusDriver.cs

@@ -6,6 +6,7 @@ using Microsoft.SPOT.Hardware;
 using Microsoft.SPOT.Messaging;
 using System.IO.Ports;
 using Samraksh.SPOT.Emulator.Network;
+using System.Collections;
 
 namespace Smart_Bus
 {
@@ -26,6 +27,7 @@ namespace Smart_Bus
 
         private static UInt16 appId;
         private static DateTime SimStart;
+        private SBMessage.MessageEndpoint messageSource;
 
         private BusDriver()
         {
@@ -40,19 +42,6 @@ namespace Smart_Bus
                 BusDriver.instance = new BusDriver();
             }
             return BusDriver.instance;
-        }
-
-        private static string BuildRouteReply(int stopId)
-        {
-            StringBuilder msg = new StringBuilder();
-            msg.Append(appId.ToString() + " ");
-            Bus bus = getInstance().myBus;
-            msg.Append(bus.id.ToString() + " ");
-            for (int i = 0; i < bus.route.StopCount; i++)
-            {
-                msg.Append(bus.route[i].stopId + "," + bus.route[i].duration + " ");
-            }
-            return msg.ToString();
         }
 
         public static void ReadNetworkPkt(byte[] msg, int size)
@@ -74,75 +63,77 @@ namespace Smart_Bus
             Debug.Print("Received message: " + msgString);
             SBMessage.MessageType msgType = message.header.type;
             Bus bus = BusDriver.getInstance().myBus;
-            switch (msgType)
+            
+            // Only handle the message if it is meant for us
+            SBMessage.MessageEndpoint msgDest = message.header.destination;
+            if (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BROADCAST ||
+                (msgDest.endptType == SBMessage.MessageEndpoint.EndpointType.BUS &&
+                    msgDest.endptId == bus.id))
             {
-                case SBMessage.MessageType.START_SIMULATION:
-                    {
-                        BusDriver.SimStart = ((PayloadDateTime)message.payload).date;
-                        Utilities.SimStart = BusDriver.SimStart;
-                        break;
-                    }
-                case SBMessage.MessageType.ROUTE_INFO_REQUEST:
-                    {
-                        int stopId = message.header.origin.srcId;
-
-                        // Only reply if we're "nearby"
-                        //  *Note: IsNearbyStop simply returns true for this project;
-                        //  this is a necessary simplification due to the deadline.
-                        // A real system would reply only if the stop is in our immediate
[…]

### 2019-04-22 Smart-Bus/RequestDriver.cs

@@ -12,7 +12,7 @@ namespace Smart_Bus
     public class RequestDriver
     {
 
-        private static int getRealSendTime(int simulationMillis)
+        private static int GetRealSendTime(int simulationMillis)
         {
             return simulationMillis / Constants.TIME_MULTIPLIER;
         }
@@ -22,6 +22,7 @@ namespace Smart_Bus
         NetInst NetPort;
         NetInst.ReceivePktCallback rcvcallBack;
 
+        IRequestPattern pattern;
         static UInt16 appId;
 
         private RequestDriver()
@@ -30,16 +31,12 @@ namespace Smart_Bus
             NetPort = new NetInst(rcvcallBack);
         }
 
-        //private void NetworkBroadcast(byte[] msg, int size)
-        //{
-        //    NetPort.Broadcast(msg, size);
-        //}
-
         private static void BuildAndSendStartSimBroadcast(DateTime startTime)
         {
-            SBMessage.MessageSource origin = new SBMessage.MessageSource(SBMessage.MessageSource.SourceType.PASSENGER);
-            SBMessage.MessageSource destination = new SBMessage.MessageSource();
-            IMessagePayload payload = new PayloadDateTime(startTime);
+            RequestDriver driver = RequestDriver.getInstance();
+            SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.PASSENGER);
+            SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint();
+            IMessagePayload payload = new PayloadSimStart(startTime, driver.pattern.numberOfBuses());
             SBMessage message = new SBMessage(SBMessage.MessageType.START_SIMULATION, origin, destination, payload);
             message.Broadcast(RequestDriver.getInstance().NetPort);
         }
@@ -47,17 +44,11 @@ namespace Smart_Bus
         private static void BuildAndSendPassengerRequest(object obj)
         {
             Request req = obj as Request;
-            SBMessage.MessageSource origin = new SBMessage.MessageSource(SBMessage.MessageSource.SourceType.PASSENGER);
-            SBMessage.MessageSource destination = new SBMessage.MessageSource(SBMessage.MessageSource.SourceType.BUS_STOP, req.origin.id);
+            SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.PASSENGER);
[…]

### 2019-04-22 Smart-Bus/RequestPattern.cs

@@ -11,7 +11,7 @@ namespace Smart_Bus
         int remainingRequests();
 
         // Gets the next request in order, and advances the cursor
-        Request getNextRequest();
+        Request NextRequest();
 
         int numberOfPassengers();
         int numberOfStops();

### 2019-04-22 Smart-Bus/RequestPattern_1P_2S_1B.cs

@@ -1,0 +1,69 @@
+using System;
+using Microsoft.SPOT;
+using Smart_Bus;
+
+namespace Smart_Bus
+{
+    class RequestPattern_1P_2S_1B: IRequestPattern
+    {
+
+        private Request[] requests = 
+        { 
+            new Request(1, 1 * 60 * 1000, 15 * 60 * 1000, 1, 2)
+        };
+        
+        private int currentRequest = 0;
+        private int numStops = 2;
+        private int numBuses = 1;
+
+        public RequestPattern_1P_2S_1B()
+        {
+            // Sort the requests array in order of earliestServingTime on startup
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
+            for (int i = 0; i < requests.Length - 1; i++)
+            {
+                int minIdx = i;
+                for (int j = i + 1; j < requests.Length; j++)
+                {
+                    if (requests[j].CompareTo(requests[minIdx]) < 0)
+                    {
+                        minIdx = j;
+                    }
+                }
+                if (minIdx != i)
+                {
+                    var temp = requests[i];
+                    requests[i] = requests[minIdx];
+                    requests[minIdx] = temp;
+                }
+            }
+        }
+
+        public int numberOfPassengers()
+        {
+            return requests.Length;
+        }
+
+        public int numberOfStops()
+        {
+            return numStops;
+        }
+
+        public int numberOfBuses()
+        {
+            return numBuses;
+        }
+
+        public int remainingRequests()
+        {
+            return requests.Length - currentRequest;
+        }
+
+        public Request NextRequest()
+        {
+            currentRequest++;
+            return requests[currentRequest - 1];
+        }
+    }
+}

### 2019-04-22 Smart-Bus/RequestPattern_2P_2S_1B.cs

@@ -1,0 +1,70 @@
+using System;
+using Microsoft.SPOT;
+using Smart_Bus;
+
+namespace Smart_Bus
+{
+    class RequestPattern_2P_2S_1B: IRequestPattern
+    {
+
+        private Request[] requests = 
+        { 
+            new Request(1, 1 * 60 * 1000, 25 * 60 * 1000, 1, 2), 
+            new Request(2, 1 * 60 * 1000, 30 * 60 * 1000, 1, 2)
+        };
+        
+        private int currentRequest = 0;
+        private int numStops = 2;
+        private int numBuses = 1;
+
+        public RequestPattern_2P_2S_1B()
+        {
+            // Sort the requests array in order of earliestServingTime on startup
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
+            for (int i = 0; i < requests.Length - 1; i++)
+            {
+                int minIdx = i;
+                for (int j = i + 1; j < requests.Length; j++)
+                {
+                    if (requests[j].CompareTo(requests[minIdx]) < 0)
+                    {
+                        minIdx = j;
+                    }
+                }
+                if (minIdx != i)
+                {
+                    var temp = requests[i];
+                    requests[i] = requests[minIdx];
+                    requests[minIdx] = temp;
+                }
+            }
+        }
+
+        public int numberOfPassengers()
+        {
+            return requests.Length;
+        }
+
+        public int numberOfStops()
+        {
+            return numStops;
+        }
+
+        public int numberOfBuses()
+        {
+            return numBuses;
+        }
+
+        public int remainingRequests()
+        {
+            return requests.Length - currentRequest;
+        }
+
+        public Request NextRequest()
+        {
+            currentRequest++;
+            return requests[currentRequest - 1];
+        }
+    }
+}

### 2019-04-22 Smart-Bus/RequestPattern_2P_4S_1B.cs

@@ -1,0 +1,70 @@
+using System;
+using Microsoft.SPOT;
+using Smart_Bus;
+
+namespace Smart_Bus
+{
+    class RequestPattern_2P_4S_1B: IRequestPattern
+    {
+
+        private Request[] requests = 
+        { 
+            new Request(1, 5 * 60 * 1000, 15 * 60 * 1000, 1, 3), 
+            new Request(2, 5 * 60 * 1000, 15 * 60 * 1000, 1, 2)
+        };
+        
+        private int currentRequest = 0;
+        private int numStops = 4;
+        private int numBuses = 1;
+
+        public RequestPattern_2P_4S_1B()
+        {
+            // Sort the requests array in order of earliestServingTime on startup
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
+            for (int i = 0; i < requests.Length - 1; i++)
+            {
+                int minIdx = i;
+                for (int j = i + 1; j < requests.Length; j++)
+                {
+                    if (requests[j].CompareTo(requests[minIdx]) < 0)
+                    {
+                        minIdx = j;
+                    }
+                }
+                if (minIdx != i)
+                {
+                    var temp = requests[i];
+                    requests[i] = requests[minIdx];
+                    requests[minIdx] = temp;
+                }
+            }
+        }
+
+        public int numberOfPassengers()
+        {
+            return requests.Length;
+        }
+
+        public int numberOfStops()
+        {
+            return numStops;
+        }
+
+        public int numberOfBuses()
+        {
+            return numBuses;
+        }
+
+        public int remainingRequests()
+        {
+            return requests.Length - currentRequest;
+        }
+
+        public Request NextRequest()
+        {
+            currentRequest++;
+            return requests[currentRequest - 1];
+        }
+    }
+}

### 2019-04-22 Smart-Bus/RequestPattern_4P_2S_2B.cs

@@ -8,11 +8,11 @@ namespace Smart_Bus
     {
 
         private Request[] requests = 
-        { 
-            new Request(1000, 2000, 0, 1), 
-            new Request(2000, 3000, 1, 0),
-            new Request(3000, 4000, 0, 1), 
-            new Request(4000, 5000, 1, 0) 
+        {
+            new Request(1, 1 * 60 * 1000, 11 * 60 * 1000, 1, 2), 
+            new Request(2, 2 * 60 * 1000, 12 * 60 * 1000, 1, 1),
+            new Request(3, 3 * 60 * 1000, 13 * 60 * 1000, 1, 2), 
+            new Request(4, 4 * 60 * 1000, 14 * 60 * 1000, 1, 1) 
         };
         
         private int currentRequest = 0;
@@ -22,7 +22,8 @@ namespace Smart_Bus
         public RequestPattern_4P_2S_2B()
         {
             // Sort the requests array in order of earliestServingTime on startup
-            // This is in-place selection sort so it's inefficient, but there won't be many requests so it's fine
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
             for (int i = 0; i < requests.Length - 1; i++)
             {
                 int minIdx = i;
@@ -62,7 +63,7 @@ namespace Smart_Bus
             return requests.Length - currentRequest;
         }
 
-        public Request getNextRequest()
+        public Request NextRequest()
         {
             currentRequest++;
             return requests[currentRequest - 1];

### 2019-04-22 Smart-Bus/RequestPattern_4P_4S_2B.cs

@@ -8,16 +8,22 @@ namespace Smart_Bus
     {
 
         private Request[] requests = 
-        { new Request(5000, 6000, 0, 1), new Request(10000, 11000, 1, 0) };
+        { 
+            new Request(1, 5 * 60 * 1000, 15 * 60 * 1000, 1, 2),
+            new Request(2, 10 * 60 * 1000, 20 * 60 * 1000, 1, 3),
+            new Request(3, 5 * 60 * 1000, 15 * 60 * 1000, 1, 4),
+            new Request(4, 10 * 60 * 1000, 20 * 60 * 1000, 1, 2)
+        };
         
         private int currentRequest = 0;
-        private int numStops = 2;
+        private int numStops = 4;
         private int numBuses = 2;
 
         public RequestPattern_4P_4S_2B()
         {
             // Sort the requests array in order of earliestServingTime on startup
-            // This is in-place selection sort so it's inefficient, but there won't be many requests so it's fine
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
             for (int i = 0; i < requests.Length - 1; i++)
             {
                 int minIdx = i;
@@ -57,7 +63,7 @@ namespace Smart_Bus
             return requests.Length - currentRequest;
         }
 
-        public Request getNextRequest()
+        public Request NextRequest()
         {
             currentRequest++;
             return requests[currentRequest - 1];

### 2019-04-22 Smart-Bus/RequestPattern_8P_2S_2B.cs

@@ -9,14 +9,14 @@ namespace Smart_Bus
 
         private Request[] requests = 
         {
-            new Request(1000, 2000, 0, 1), 
-            new Request(2000, 3000, 1, 0),
-            new Request(3000, 4000, 0, 1), 
-            new Request(4000, 5000, 1, 0),
-            new Request(1000, 2000, 1, 0), 
-            new Request(2000, 3000, 0, 1),
-            new Request(3000, 4000, 1, 0), 
-            new Request(4000, 5000, 0, 1) 
+            new Request(1, 1 * 60 * 1000, 12 * 60 * 1000, 1, 2), 
+            new Request(2, 2 * 60 * 1000, 13 * 60 * 1000, 1 ,2),
+            new Request(3, 3 * 60 * 1000, 14 * 60 * 1000, 1, 2), 
+            new Request(4, 4 * 60 * 1000, 15 * 60 * 1000, 1, 2),
+            new Request(5, 1 * 60 * 1000, 11 * 60 * 1000, 1, 2), 
+            new Request(6, 2 * 60 * 1000, 12 * 60 * 1000, 1, 2),
+            new Request(7, 3 * 60 * 1000, 13 * 60 * 1000, 1, 2), 
+            new Request(8, 4 * 60 * 1000, 14 * 60 * 1000, 1, 2) 
         };
         
         private int currentRequest = 0;
@@ -26,7 +26,8 @@ namespace Smart_Bus
         public RequestPattern_8P_2S_2B()
         {
             // Sort the requests array in order of earliestServingTime on startup
-            // This is in-place selection sort so it's inefficient, but there won't be many requests so it's fine
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
             for (int i = 0; i < requests.Length - 1; i++)
             {
                 int minIdx = i;
@@ -66,7 +67,7 @@ namespace Smart_Bus
             return requests.Length - currentRequest;
         }
 
-        public Request getNextRequest()
+        public Request NextRequest()
         {
             currentRequest++;
             return requests[currentRequest - 1];

### 2019-04-22 Smart-Bus/RequestPattern_8P_8S_4B.cs

@@ -4,23 +4,30 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_2P_2S_2B: IRequestPattern
+    class RequestPattern_8P_8S_4B: IRequestPattern
     {
 
         private Request[] requests = 
-        { 
-            new Request(5000, 6000, 0, 1), 
-            new Request(10000, 11000, 1, 0)
+        {
+            new Request(1, 1 * 1000, 11 * 1000, 1, 5), 
+            new Request(2, 2 * 1000, 12 * 1000, 1 ,8),
+            new Request(3, 3 * 1000, 13 * 1000, 1, 2), 
+            new Request(4, 4 * 1000, 14 * 1000, 1, 6),
+            new Request(5, 5 * 1000, 15 * 1000, 1, 5), 
+            new Request(6, 6 * 1000, 16 * 1000, 1, 4),
+            new Request(7, 7 * 1000, 17 * 1000, 1, 2), 
+            new Request(8, 8 * 1000, 18 * 1000, 1, 7) 
         };
         
         private int currentRequest = 0;
-        private int numStops = 2;
-        private int numBuses = 2;
+        private int numStops = 8;
+        private int numBuses = 4;
 
-        public RequestPattern_2P_2S_2B()
+        public RequestPattern_8P_8S_4B()
         {
             // Sort the requests array in order of earliestServingTime on startup
-            // This is in-place selection sort so it's inefficient, but there won't be many requests so it's fine
+            // This is in-place selection sort so it's inefficient, but there 
+            // won't be many requests during testing so it's fine
             for (int i = 0; i < requests.Length - 1; i++)
             {
                 int minIdx = i;
@@ -60,7 +67,7 @@ namespace Smart_Bus
             return requests.Length - currentRequest;
         }
 
-        public Request getNextRequest()
+        public Request NextRequest()
         {
             currentRequest++;
             return requests[currentRequest - 1];

### 2019-04-22 Smart-Bus/Utilities/Bus.cs

@@ -16,73 +16,20 @@ namespace Smart_Bus
         public int busStartTime; //ts_k: expected start time at terminus 
         public int busEndTime; //te_k: expected end time terminus
         public Route route;
+        public const int START_TIME = 0;
+        public const int END_TIME = 100000;
+        public const int CAPACITY = 5;
+        public const int TERMINUS = -1;
         //public Request_v[] routeInfo;
 
-        public Bus(int id, int terminusId, int busStartTime, int busEndTime)
+        public Bus(int id)
         {
             this.id = id;
-            this.availCapacity = capacity;
-            this.terminusLocation = terminusId;
-            this.busStartTime = busStartTime;
-            this.busEndTime = busEndTime;
+            this.availCapacity = CAPACITY;
+            this.terminusLocation = TERMINUS;
+            this.busStartTime = START_TIME;
+            this.busEndTime = END_TIME;
             this.route = new Route();
-        }
-
-        public int StopsUntilEncounter(int stopId)
-        {
-            BusStatus currLoc = this.StatusAtTime(DateTime.Now);
-            int stopsUntilEncounter = -1;
-            for (int i = currLoc.routeIdx; i < this.route.StopCount && stopsUntilEncounter < 0; i++)
-            {
-                if (this.route[i].stopId == stopId)
-                {
-                    stopsUntilEncounter = i - currLoc.routeIdx;
-                }
-            }
-            return stopsUntilEncounter;
-        }
-
-        public BusStatus StatusAtTime(DateTime time)
-        {
-            BusStatus currStatus = new BusStatus();
-            TimeSpan elapsedTime = time - this.simStartTime;
-            int realElapsedMillis = (int)elapsedTime.Milliseconds;
-            int simElapsedMillis = realElapsedMillis / Constants.TIME_MULTIPLIER;
-            int computeTime = busStartTime;
-            int computeCap = capacity;
-            int i = 0;
-            while (computeTime < simElapsedMillis)
-            {
-                RouteStop stop = this.route[i];
-                computeTime += stop.duration;
-                computeCap += stop.capDelta;
-
-                if (computeTime > simElapsedMillis)
-                {
-                    // We're currently waiting at a stop
-                    currStatus.previousStop = stop.stopId;
-                    currStatus.nextStop = stop.stopId;
-                    currStatus.timeRemainingInState = computeTime - simElapsedMillis;
-                    currStatus.routeIdx = i;
-                    currStatus.capacity = computeCap;
-                }
[…]

### 2019-04-22 Smart-Bus/Utilities/BusStop.cs

@@ -4,92 +4,72 @@ using Microsoft.SPOT;
 using System.Collections;
 
 namespace Smart_Bus
-{   
-    public class BusStop
+{
+    public struct Bus_info
     {
+        public int busId;
+        public const int capacity = 5;
+        public int terminusLocation;
+        public int busStartTime; //ts_k: expected start time at terminus 
+        public int busEndTime; //te_k: expected end time terminus
+        public int NumServed;
+        public Request_v[] routeInfo;
+        public Request_v[] pending_routeInfo;
+    }
+
+    public enum BusStop_State
+    {
+        REQUEST_NULL = 0,
+        REQUEST_WAIT_FOR_ROUTE_INFO = 1,
+        REQUEST_READY_TO_BE_ASSIGNED = 2,
+        REQUEST_WAIT_FOR_TIMER = 3,
+        REQUEST_ASSIGNED_AND_SENDING_TO_BUS = 4
+    }
+    
+    public class BusStop
+    {   
         public int id;
-        public Bus[] busInfo_list;
+        public BusStop_State stop_state;
+        public Bus_info[] bus_list;
         public Request[] request_list;
+        public int pending_request_index;
         public const int urgencyThreshold = 300000; //5 minutes
         public DateTime SimStart;
+        public int numBuses;
+        public int num_route_info_rsp_rcvd;
 
         public BusStop(int id)
         {
             this.id = id;
+            this.stop_state = BusStop_State.REQUEST_NULL;
+            this.pending_request_index = -1;
+            this.numBuses = 0;
+            this.num_route_info_rsp_rcvd = 0;
         }
 
-        public void request_receive(Request new_request, bool delay)
+        public void Receive_request(Request new_request)
         {
-            TimeSpan elapsedTime = DateTime.Now - SimStart;
-            int simulationMillis = (int)elapsedTime.Milliseconds;
+            //TimeSpan elapsedTime = DateTime.Now - SimStart;
+            //int simulationMillis = (int)elapsedTime.Milliseconds;
 
             Debug.Print("Received new request");
+            Debug.Print("Request ID" + new_request.origin.requestId);
             Debug.Print("Origin: " + new_request.origin.stop.id + ", Destination: " + new_request.destination.stop.id);
             Debug.Print("EarliestPickupTime: " + new_request.origin.earliestServingTime + ", LatestPickupTime: " + new_request.origin.latestServingTime);
[…]

### 2019-04-22 Smart-Bus/Utilities/Constants.cs

@@ -5,17 +5,18 @@ namespace Smart_Bus
 {
     public class Constants
     {
-        // Every hop between bus stops is constant; for this demo, it takes 1 simulated minute
-        public static readonly int HOP_DURATION = 60000;
-        public static readonly int STOP_DURATION = 10000;
+        // Every hop between bus stops is constant; for this demo, it takes 3 simulated minutes
+        public static readonly int HOP_DURATION = 3 * 60 * 1000;
+        public static readonly int STOP_DURATION = 30 * 1000;
 
         // 1 is Real Time (i.e., one second of wall time per second of simulation time)
         // Suggested values are on the order of 100 (every 10 milliseconds of wall time is one second of simulation time)
-        public static readonly int TIME_MULTIPLIER = 100;
+        public static readonly int TIME_MULTIPLIER = 1;
 
         // DateTime format string for all messages
         public static string DATE_TIME_FORMAT = "yyyy'-'MM'-'dd'T'H':'mm':'ss.fff";
         public static char[] DATE_FORMAT_SEPARATORS = new char[] { '-', 'T', ':', '.' };
+        public static int BUS_START_TIME;
         public enum DateComponentPositions
         {
             YEAR = 0,

### 2019-04-22 Smart-Bus/Utilities/IMessagePayload.cs

@@ -7,10 +7,12 @@ namespace Smart_Bus
     {
         // Implemented by:
         //  Request
+        //  Request_v
         //  Route
         //  PayloadDateTime
         //  PayloadSimpleString
         //  PayloadRouteRequestForward
+        //  PayloadRouteChangeAckResponse
 
         string BuildPayload();
     }

### 2019-04-22 Smart-Bus/Utilities/PayloadDateTime.cs

@@ -1,46 +1,0 @@
-using System;
-using Microsoft.SPOT;
-
-namespace Smart_Bus
-{
-    public class PayloadDateTime : IMessagePayload
-    {
-        public DateTime date;
-
-        public static PayloadDateTime Now
-        {
-            get { return new PayloadDateTime(DateTime.Now); }
-            private set { }
-        }
-
-        public PayloadDateTime(DateTime date)
-        {
-            this.date = date;
-        }
-
-        public PayloadDateTime(string[] payload, ref int startIdx)
-        {
-            this.date = Utilities.ParseDateTime(payload[startIdx++]);
-        }
-
-        public static TimeSpan operator -(PayloadDateTime pd, DateTime d)
-        {
-            return pd.date - d;
-        }
-
-        public static TimeSpan operator -(PayloadDateTime pd1, PayloadDateTime pd2)
-        {
-            return pd1.date - pd2.date;
-        }
-
-        public static TimeSpan operator -(DateTime d, PayloadDateTime pd)
-        {
-            return d - pd.date;
-        }
-
-        public string BuildPayload()
-        {
-            return this.date.ToString(Constants.DATE_TIME_FORMAT);
-        }
-    }
-}

### 2019-04-22 Smart-Bus/Utilities/PayloadRouteChangeAckResponse.cs

@@ -22,7 +22,7 @@ namespace Smart_Bus
 
         public string BuildPayload()
         {
-            return (didAcceptRouteChange ? "1" : "0") + " " + latestRoute.ToString();
+            return (didAcceptRouteChange ? "1 " : "0 ") + latestRoute.BuildPayload();
         }
     }
 }

### 2019-04-22 Smart-Bus/Utilities/PayloadSimStart.cs

@@ -1,0 +1,28 @@
+using System;
+using Microsoft.SPOT;
+
+namespace Smart_Bus
+{
+    public class PayloadSimStart : IMessagePayload
+    {
+        public DateTime date;
+        public int numBuses;
+
+        public PayloadSimStart(DateTime date, int numBuses)
+        {
+            this.date = date;
+            this.numBuses = numBuses;
+        }
+
+        public PayloadSimStart(string[] messageComponents, ref int startIdx)
+        {
+            this.date = Utilities.ParseDateTime(messageComponents[startIdx++]);
+            this.numBuses = int.Parse(messageComponents[startIdx++]);
+        }
+
+        public string BuildPayload()
+        {
+            return this.date.ToString(Constants.DATE_TIME_FORMAT) + " " + this.numBuses.ToString() + " ";
+        }
+    }
+}

### 2019-04-22 Smart-Bus/Utilities/PayloadSimpleString.cs

@@ -20,7 +20,7 @@ namespace Smart_Bus
 
         public string BuildPayload()
         {
-            throw new NotImplementedException();
+            return this.str + " ";
         }
     }
 }

### 2019-04-22 Smart-Bus/Utilities/Request.cs

@@ -1,30 +1,48 @@
 using System;
 using System.Threading;
 using Microsoft.SPOT;
+using System.Text;
 
 namespace Smart_Bus
 {
     public class Request : IComparable, IMessagePayload
     {
+        public int requestId;
         public int requestSendTime;
         public Request_v origin;
         public Request_v destination;
         public bool delay;
 
-        public Request(int earliestPickupTime, int latestDeliveryTime, int origin, int destination)
+        public Request(int requestId, int earliestPickupTime, int latestDeliveryTime, int origin, int destination)
         {
             BusStop originStop = new BusStop(origin);
             BusStop destStop = new BusStop(destination);
-            int latestPickupTime = latestDeliveryTime - TravelTime(originStop, destStop);
-            int earliestDeliveryTime = earliestPickupTime + TravelTime(originStop, destStop);
+            int latestPickupTime = latestDeliveryTime - Utilities.TravelTime(originStop, destStop);
+            int earliestDeliveryTime = earliestPickupTime + Utilities.TravelTime(originStop, destStop);
 
+            this.requestId = requestId;
             this.requestSendTime = earliestPickupTime;
-            this.origin = new Request_v(earliestPickupTime, latestPickupTime, true, originStop, false);
-            this.destination = new Request_v(earliestDeliveryTime, latestDeliveryTime, false, destStop, false);
+            this.origin = new Request_v(
+                requestId,
+                earliestPickupTime,
+                latestPickupTime,
+                true,
+                originStop,
+                false);
+            this.destination = new Request_v(
+                requestId,
+                earliestDeliveryTime,
+                latestDeliveryTime,
+                false,
+                destStop,
+                false);
         }
 
         public Request(Request_v origin, Request_v destination)
         {
+            Debug.Assert(origin.requestId == destination.requestId);
+
+            this.requestId = origin.requestId;
             this.requestSendTime = origin.earliestServingTime;
             this.origin = origin;
             this.destination = destination;
@@ -36,6 +54,7 @@ namespace Smart_Bus
             //  [earliestPickupTime, latestDeliveryTime, origin, destination]
             // where the times are in ms since simulation start
 
+            int requestId = int.Parse(messageComponents[startIdx++]);
             int earliestPickupTime = int.Parse(messageComponents[startIdx++]);
             int latestDeliveryTime = int.Parse(messageComponents[startIdx++]);
[…]

### 2019-04-22 Smart-Bus/Utilities/Route.cs

@@ -7,283 +7,150 @@ namespace Smart_Bus
 {
     public class Route : IMessagePayload
     {
-        IList stops;
-        IList requests;
+        IList importantStops;
 
-        private struct RouteBuilderPair
+        // NumServed marks served requests as such, in addition to
+        //  computing the number of served requests.
+        public int NumServed
         {
-            public Request_v origin;
-            public int requestId;
-
-            public RouteBuilderPair(Request_v origin, int requestId)
+            get
             {
-                this.origin = origin;
-                this.requestId = requestId;
+                int simElapsedMillis = Utilities.ElapsedSimulationMillis();
+                int computeTime = Bus.START_TIME;
+                int i = 0;
+                int servedCount = 0;
+                while (i < this.importantStops.Count - 1 && computeTime < simElapsedMillis)
+                {
+                    Request_v stop = this[i];
+                    computeTime = System.Math.Max(computeTime, stop.earliestServingTime) + Constants.STOP_DURATION;
+                    if (computeTime < simElapsedMillis)
+                    {
+                        // We still haven't gotten to the last request we've served, 
+                        //  so compute how long it will take to get to the next stop
+                        servedCount++;
+                        stop.served = true;
+                        Request_v nextStop = this[i + 1];
+                        computeTime += Utilities.TravelTime(stop.stop, nextStop.stop);
+                    }
+                    i++;
+                }
+                return servedCount;
             }
         }
 
-        public int StopCount
+        public int Count
         {
-            get { return this.stops.Count; }
-            private set { }
-        }
-
-        public int RequestCount
-        {
-            get { return this.requests.Count; }
-            private set { }
+            get { return this.importantStops.Count; }
         }
 
         public Route()
         {
-            this.stops = new ArrayList();
-            this.requests = new ArrayList();
+            this.importantStops = new ArrayList();
+            //BusStop terminusStop = new BusStop(Bus.TERMINUS);
+            //Request_v terminusStart = new Request_v(-1, Bus.START_TIME, Bus.END_TIME, true, terminusStop, false);
+            //Request_v terminusEnd = new Request_v(-1, Bus.START_TIME, Bus.END_TIME, false, terminusStop, false);
+            //this.importantStops.Add(terminusStart);
+            //this.importantStops.Add(terminusEnd);
         }
 
-        public Route(Request_v[] importantStops, int[] requestIds)
+        public Route(Request_v[] arr)
         {
[…]

### 2019-04-22 Smart-Bus/Utilities/SBMessage.cs

@@ -11,34 +11,34 @@ namespace Smart_Bus
 {
     public class SBMessage
     {
-        public struct MessageSource
+        public struct MessageEndpoint
         {
-            public enum SourceType
+            public enum EndpointType
             {
                 BROADCAST = 0,
                 PASSENGER = 1,
                 BUS_STOP = 2,
                 BUS = 3
             }
-            public SourceType srcType;
-            public int srcId;
+            public EndpointType endptType;
+            public int endptId;
 
             // Initializer defaults to BROADCAST with no id
-            public MessageSource(string srcType = "0", string srcId = "-1")
+            public MessageEndpoint(string endptType = "0", string endptId = "-1")
             {
-                this.srcType = (SourceType)int.Parse(srcType);
-                this.srcId = int.Parse(srcId);
+                this.endptType = (EndpointType)int.Parse(endptType);
+                this.endptId = int.Parse(endptId);
             }
 
-            public MessageSource(SourceType srcType = SourceType.BROADCAST, int srcId = -1)
+            public MessageEndpoint(EndpointType endptType = EndpointType.BROADCAST, int endptId = -1)
             {
-                this.srcType = srcType;
-                this.srcId = srcId;
+                this.endptType = endptType;
+                this.endptId = endptId;
             }
 
             public override string ToString()
             {
-                return this.srcType.ToString() + " " + this.srcId.ToString();
+                return this.endptType.ToString() + " " + this.endptId.ToString();
             }
         }
 
@@ -47,19 +47,19 @@ namespace Smart_Bus
             public const int Length = 5;
 
             public MessageType type;
-            public MessageSource origin;
-            public MessageSource destination;
+            public MessageEndpoint source;
+            public MessageEndpoint destination;
 
-            public MessageHeader(MessageType type, MessageSource origin, MessageSource destination)
+            public MessageHeader(MessageType type, MessageEndpoint source, MessageEndpoint destination)
             {
                 this.type = type;
-                this.origin = origin;
+                this.source = source;
                 this.destination = destination;
             }
 
             public override string ToString()
             {
-                return type.ToString() + " " + origin.ToString() + " " + destination.ToString();
+                return type.ToString() + " " + source.ToString() + " " + destination.ToString();
             }
         }
 
@@ -77,56 +77,71 @@ namespace Smart_Bus
             ROUTE_CHANGE_ACK = 31
         }
 
-        public MessageHeader header;
-        public IMessagePayload payload;
[…]

### 2019-04-22 Smart-Bus/Utilities/Utilities.cs

@@ -1,6 +1,7 @@
 using System;
 using System.Text;
 using Microsoft.SPOT;
+using System.Threading;
 
 namespace Smart_Bus
 {
@@ -10,16 +11,29 @@ namespace Smart_Bus
 
         public static int ElapsedMillis()
         {
-            TimeSpan elapsedTime = DateTime.Now - SimStart;
-            return (int)elapsedTime.Milliseconds;
+            return (int)((DateTime.Now.Ticks - SimStart.Ticks) / TimeSpan.TicksPerMillisecond);
+            //TimeSpan elapsedTime = DateTime.Now - SimStart;
+            //return (int)elapsedTime.TotalMilliseconds;
+        }
+
+        public static int ElapsedSimulationMillis()
+        {
+            return ElapsedMillis() * Constants.TIME_MULTIPLIER;
         }
 
         public static void Main(String[] args)
         {
             Debug.Print("Use this for simple testing of Utilities methods");
 
-            DateTime foo = Utilities.ParseDateTime("2019-04-16T16:24:01.234");
-            Debug.Print(foo.ToString());
+            //SimStart = DateTime.Now;
+            //Debug.Print(SimStart.ToString(Constants.DATE_TIME_FORMAT));
+            //Thread.Sleep(1500);
+            //Debug.Print("Milliseconds btwn " + SimStart.ToString(Constants.DATE_TIME_FORMAT) + " to " + DateTime.Now.ToString(Constants.DATE_TIME_FORMAT) + ": " + ElapsedMillis());
+            //Thread.Sleep(Timeout.Infinite);
+
+            SBMessage message = new SBMessage("30 0 0 2 1 ");
+            Route r = (Route)message.payload;
+            Debug.Print("<" + r.BuildPayload() + ">");
         }
 
         public static byte[] StringToByteArray(String s)
@@ -42,9 +56,19 @@ namespace Smart_Bus
             return s.ToString();
         }
 
+        public static int TravelTime(BusStop origin, BusStop destination)
+        {
+            // travel time = hopcount * Constants.HOP_DURATION (ms)
+            // TODO: compute this from graph topology -- BFS?
+
+            return System.Math.Abs(origin.id - destination.id) * Constants.HOP_DURATION;
+        }
+
+
         public static DateTime ParseDateTime(string payload)
         {
             // Unfortunately there are no built-in parsers for DateTime in the MicroFramework, so I made my own.
[…]

### 2019-04-22 Report/paper.tex
Adding to Paper
Completed section on static approach

@@
 
+\subsubsection{Emulator Networking Bugs}
+It was discovered near the end of our validation process that there is a bug in the Samraksh Emulator's networking protocol: if two messages arrive to the hub at approximately the same time, there seems to be a high likelihood that they will be merged into a single message, sent to some or all nodes.
+This, of course, poses a huge difficulty to reliably testing the application (or even running it at all).
+It is for this reason that we are unable to produce a demonstration of a complex network of buses and bus stops.
+
+\subsubsection{Software Design Decisions}
+There were some decisions made during the design process which were, in hindsight, ill-advised.
+Specifically, the handling of non-urgent requests dispatches a timer in a different project than that in which messages are received and sent.
+The problem with this is that in C\# projects cannot have ``circular dependencies'', and thus there is no good way to call back to the messaging service once the timer has completed.
+Therefore, while the request is being assigned correctly by the timer callback once the request has become urgent, it will not notify the bus of this fact.
+As a workaround as the deadline approached, a decision was made to treat \emph{all} requests as urgent; this avoids the timer and keeps the appropriate information around with which to send a \lstinline{ROUTE_CHANGE_REQUEST} message to the appropriate bus.
+
 \subsection{Testing and Evaluation}
@@
 Its efficacy was evaluated from a purely theoretical standpoint; there is no implementation of the static algorithm.
-For each Request Pattern on which the Smart-Bus algorithm was tested, the minimum number of buses required by the Traversal approach to serve those requests on time (or, with minimal lateness) was computed.
-The results are summarized in Table~\ref{tbl:traversal} below.
 
-The method for computing the values in the table is quite simple, given the assumptions made about the toplogy and travel time between stops.
+The method for computing the minimunm number of buses and total lateness using the traversal approach is quite simple, given the assumptions made about the toplogy and travel time between stops.
 For a traversing bus $B_i$, its route $R = \langle 0, 1, 2, \dots, N-1, N, N-1, N-2, \dots, 1, 0, 1, 2, \dots \rangle$, repeated until the total travel time is greater than its operating window: $T_{B_i} > (l_0 - e_0)$.
 Thus, given a system with hop duration $H$ and stop duration $S$, the number of stops along a bus's route is $B_S = \frac{l_0 - e_0}{H + S} + 1$ and the number of traversals made by a bus is $B_T = \frac{B_S}{N}$, and the time it takes for a traversal in a system with $N$ stops is $T_N = N (H + S) + S$.
+In this model, buses start at a passenger stop, not a terminus.
+As an example, in a traversal system using two buses, each will start the the opposite end of the line, and travel towards each other to start.
 
@@
 Request Pattern & Min \# of Buses & Total Lateness \\ \hline
-2P\_2B\_2S & ? & ?\\
-4P\_2B\_2S & ? & ?\\
-6P\_4B\_4S & ? & ?\\
-8P\_4B\_8S & ? & ?\\
+1P\_2S\_1B & $1$ & $-8$ \\
+2P\_2S\_1B & $1$ & $-1$ \\
+2P\_4S\_1B & $2$ & $5$ \\
 \hline
@@
 \end{table}
+
+Care was taken when devising the Request Patterns not to intentionally disadvantage the static approach.
+Considerations made include accounting for the fact that, in the real world, passengers will be aware of the schedule and will appear at stops approximately when a bus would be there.
+However, the results to point to the fact that the Smart Bus algorithm improves on the traversal approach for these patterns.
 

### 2019-04-22 Bus-Stop/BusStopDriver.cs
Heavily commented non-BusStop code

@@ -59,8 +59,8 @@ namespace Smart_Bus
         {
 
             string msgString = Utilities.ByteArrayToString(msg);
-            SBMessage message = new SBMessage(msgString);
             Debug.Print("Received message: " + msgString);
+            SBMessage message = new SBMessage(msgString);
             SBMessage.MessageType msgType = message.header.type;
             BusStop stop = BusStopDriver.getInstance().myBusStop;
 

### 2019-04-22 Bus/BusDriver.cs

@@ -12,11 +12,6 @@ namespace Smart_Bus
 {
     public class BusDriver
     {
-        private static int getRealSendTime(int simulationMillis)
-        {
-            return simulationMillis / Constants.TIME_MULTIPLIER;
-        }
-
         private static BusDriver instance;
 
         // Requires an id, which is equivalent to appId, so do not create bus until after appId is initialized
@@ -59,8 +54,8 @@ namespace Smart_Bus
             //     reply, then ignore it.
 
             string msgString = Utilities.ByteArrayToString(msg);
-            SBMessage message = new SBMessage(msgString);
             Debug.Print("Received message: " + msgString);
+            SBMessage message = new SBMessage(msgString);
             SBMessage.MessageType msgType = message.header.type;
             Bus bus = BusDriver.getInstance().myBus;
             
@@ -93,7 +88,6 @@ namespace Smart_Bus
                             {
                                 // A bus stop is asking for route information
                                 // from "nearby" buses, and we're one of them
-
                                 IMessagePayload replyPayload = bus.route;
                                 SBMessage reply = new SBMessage(
                                     SBMessage.MessageType.ROUTE_INFO_RESPONSE,
@@ -109,8 +103,8 @@ namespace Smart_Bus
                             Route newRoute = message.payload as Route;
                             bool confirm = false;
 
-                            // I believe the only way we this won't be true here is if
-                            //  another stop has changed our route since this stop last
+                            // The only way we this won't be true here is if another
+                            //  stop has changed our route since this stop last
                             //  received info about our route.
                             if (bus.HasCapacityNow())
                             {
@@ -146,7 +140,10 @@ namespace Smart_Bus
             Debug.Print("Successfully got ID from the Hub: " + appId.ToString());
 
             instance.myBus = new Bus(appId);
-            instance.messageSource = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS, appId);
+            
+            // Keep the message source around so we don't have to write this monstrosity all the time
+            instance.messageSource = 
+                new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS, appId);
 
             Thread.Sleep(Timeout.Infinite);
         }

### 2019-04-22 Smart-Bus/RequestDriver.cs

@@ -11,12 +11,6 @@ namespace Smart_Bus
 {
     public class RequestDriver
     {
-
-        private static int GetRealSendTime(int simulationMillis)
-        {
-            return simulationMillis / Constants.TIME_MULTIPLIER;
-        }
-
         private static RequestDriver instance;
 
         NetInst NetPort;
@@ -33,8 +27,11 @@ namespace Smart_Bus
 
         private static void BuildAndSendStartSimBroadcast(DateTime startTime)
         {
+            // Broadcast the simulation start time; this ensures that all nodes stay in sync
+
             RequestDriver driver = RequestDriver.getInstance();
-            SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.PASSENGER);
+            SBMessage.MessageEndpoint origin = 
+                new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.PASSENGER);
             SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint();
             IMessagePayload payload = new PayloadSimStart(startTime, driver.pattern.numberOfBuses());
             SBMessage message = new SBMessage(SBMessage.MessageType.START_SIMULATION, origin, destination, payload);
@@ -43,6 +40,8 @@ namespace Smart_Bus
 
         private static void BuildAndSendPassengerRequest(object obj)
         {
+            // Send a Passenger Request to the request's origin bus stop
+
             Request req = obj as Request;
             SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.PASSENGER);
             SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS_STOP, req.origin.stop.id);
@@ -72,7 +71,7 @@ namespace Smart_Bus
         public static void Main()
         {
             RequestDriver driver = RequestDriver.getInstance();
-            driver.pattern = new RequestPattern_1P_2S_1B();
+            driver.pattern = new RequestPattern_2P_2S_1B();
             driver.NetPort.Init();
             Thread.Sleep(100);
             appId = driver.NetPort.GetID();
@@ -82,13 +81,15 @@ namespace Smart_Bus
             Utilities.SimStart = startTime;
             BuildAndSendStartSimBroadcast(startTime);
             Debug.Print("startTime = " + startTime.ToString("HH:mm:ss.fff"));
[…]

### 2019-04-22 Smart-Bus/RequestPattern.cs

@@ -13,7 +13,9 @@ namespace Smart_Bus
         // Gets the next request in order, and advances the cursor
         Request NextRequest();
 
+        // Returns the total number of requests in this pattern
         int numberOfPassengers();
+
         int numberOfStops();
         int numberOfBuses();
     }

### 2019-04-22 Smart-Bus/RequestPattern_1P_2S_1B.cs

@@ -4,6 +4,7 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
+    // Request Pattern with 1 passenger, 2 stops, and 1 bus
     class RequestPattern_1P_2S_1B: IRequestPattern
     {
 

### 2019-04-22 Smart-Bus/RequestPattern_2P_2S_1B.cs

@@ -4,13 +4,14 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_2P_2S_1B: IRequestPattern
+    // Request Pattern with 2 passenger, 2 stops, and 1 bus
+    class RequestPattern_2P_2S_1B : IRequestPattern
     {
 
         private Request[] requests = 
         { 
-            new Request(1, 1 * 60 * 1000, 25 * 60 * 1000, 1, 2), 
-            new Request(2, 1 * 60 * 1000, 30 * 60 * 1000, 1, 2)
+            new Request(1, 5 * 60 * 1000, 12 * 60 * 1000, 1, 2), 
+            new Request(2, 10 * 60 * 1000, 17 * 60 * 1000, 2, 1)
         };
         
         private int currentRequest = 0;

### 2019-04-22 Smart-Bus/RequestPattern_2P_4S_1B.cs

@@ -4,13 +4,14 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_2P_4S_1B: IRequestPattern
+    // Request Pattern with 2 passengers, 4 stops, and 1 bus
+    class RequestPattern_2P_4S_1B : IRequestPattern
     {
 
         private Request[] requests = 
         { 
             new Request(1, 5 * 60 * 1000, 15 * 60 * 1000, 1, 3), 
-            new Request(2, 5 * 60 * 1000, 15 * 60 * 1000, 1, 2)
+            new Request(2, 5 * 60 * 1000, 15 * 60 * 1000, 4, 2)
         };
         
         private int currentRequest = 0;

### 2019-04-22 Smart-Bus/RequestPattern_4P_2S_2B.cs

@@ -4,15 +4,16 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_4P_2S_2B: IRequestPattern
+    // Request Pattern with 4 passengers, 2 stops, and 2 buses
+    class RequestPattern_4P_2S_2B : IRequestPattern
     {
 
         private Request[] requests = 
         {
             new Request(1, 1 * 60 * 1000, 11 * 60 * 1000, 1, 2), 
-            new Request(2, 2 * 60 * 1000, 12 * 60 * 1000, 1, 1),
+            new Request(2, 2 * 60 * 1000, 12 * 60 * 1000, 2, 1),
             new Request(3, 3 * 60 * 1000, 13 * 60 * 1000, 1, 2), 
-            new Request(4, 4 * 60 * 1000, 14 * 60 * 1000, 1, 1) 
+            new Request(4, 4 * 60 * 1000, 14 * 60 * 1000, 2, 1) 
         };
         
         private int currentRequest = 0;

### 2019-04-22 Smart-Bus/RequestPattern_4P_4S_2B.cs

@@ -4,15 +4,16 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_4P_4S_2B: IRequestPattern
+    // Request Pattern with 4 passengers, 4 stops, and 2 buses
+    class RequestPattern_4P_4S_2B : IRequestPattern
     {
 
         private Request[] requests = 
         { 
             new Request(1, 5 * 60 * 1000, 15 * 60 * 1000, 1, 2),
-            new Request(2, 10 * 60 * 1000, 20 * 60 * 1000, 1, 3),
+            new Request(2, 10 * 60 * 1000, 20 * 60 * 1000, 4, 3),
             new Request(3, 5 * 60 * 1000, 15 * 60 * 1000, 1, 4),
-            new Request(4, 10 * 60 * 1000, 20 * 60 * 1000, 1, 2)
+            new Request(4, 10 * 60 * 1000, 20 * 60 * 1000, 3, 2)
         };
         
         private int currentRequest = 0;

### 2019-04-22 Smart-Bus/RequestPattern_8P_2S_2B.cs

@@ -4,7 +4,8 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_8P_2S_2B: IRequestPattern
+    // Request Pattern with 8 passengers, 2 stops, and 2 bus
+    class RequestPattern_8P_2S_2B : IRequestPattern
     {
 
         private Request[] requests = 

### 2019-04-22 Smart-Bus/RequestPattern_8P_8S_4B.cs

@@ -4,18 +4,19 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    class RequestPattern_8P_8S_4B: IRequestPattern
+    // Request Pattern with 8 passengers, 8 stops, and 4 bus
+    class RequestPattern_8P_8S_4B : IRequestPattern
     {
 
         private Request[] requests = 
         {
             new Request(1, 1 * 1000, 11 * 1000, 1, 5), 
-            new Request(2, 2 * 1000, 12 * 1000, 1 ,8),
-            new Request(3, 3 * 1000, 13 * 1000, 1, 2), 
-            new Request(4, 4 * 1000, 14 * 1000, 1, 6),
-            new Request(5, 5 * 1000, 15 * 1000, 1, 5), 
-            new Request(6, 6 * 1000, 16 * 1000, 1, 4),
-            new Request(7, 7 * 1000, 17 * 1000, 1, 2), 
+            new Request(2, 2 * 1000, 12 * 1000, 4 ,8),
+            new Request(3, 3 * 1000, 13 * 1000, 6, 2), 
+            new Request(4, 4 * 1000, 14 * 1000, 3, 6),
+            new Request(5, 5 * 1000, 15 * 1000, 4, 5), 
+            new Request(6, 6 * 1000, 16 * 1000, 8, 4),
+            new Request(7, 7 * 1000, 17 * 1000, 7, 2), 
             new Request(8, 8 * 1000, 18 * 1000, 1, 7) 
         };
         

### 2019-04-22 Smart-Bus/Request_OLD.cs

@@ -1,38 +1,0 @@
-using System;
-using System.Threading;
-using Microsoft.SPOT;
-using Smart_Bus;
-
-namespace Smart_Bus
-{
-    public class Request_OLD : IComparable
-    {
-        public int earliestServingTime;
-        public int latestServingTime;
-        public BusStop origin;
-        public BusStop destination;
-
-        public Request_OLD(int earliestServingTime, int latestServingTime, int origin, int destination)
-        {
-            this.earliestServingTime = earliestServingTime;
-            this.latestServingTime = latestServingTime;
-            this.origin = new BusStop(origin);
-            this.destination = new BusStop(destination);
-        }
-
-        public int CompareTo(object obj)
-        {
-            if (obj == null) return 1;
-
-            Request_OLD other = obj as Request_OLD;
-            if (other != null)
-            {
-                return System.Math.Sign(this.earliestServingTime - other.earliestServingTime);
-            }
-            else
-            {
-                throw new ArgumentException("obj is not a Request");
-            }
-        }
-    }
-}

### 2019-04-22 Smart-Bus/Utilities/Bus.cs

@@ -20,7 +20,6 @@ namespace Smart_Bus
         public const int END_TIME = 100000;
         public const int CAPACITY = 5;
         public const int TERMINUS = -1;
-        //public Request_v[] routeInfo;
 
         public Bus(int id)
         {
@@ -34,6 +33,11 @@ namespace Smart_Bus
 
         public bool IsNearbyStop(int stopId)
         {
+            // Return true now as a simplification. A real system would use something
+            //  like the commented lines, in conjunction with BFS, to find all nearby
+            //  buses in the network. StopsUntilEncounter computes the number of hops
+            //  this bus must make before it arrives at stop stopId in its route.
+
             //int stopsUntilEncounter = this.StopsUntilEncounter(stopId);
             //return 0 <= stopsUntilEncounter && stopsUntilEncounter < NearbyThreshold;
             return true;
@@ -41,6 +45,8 @@ namespace Smart_Bus
 
         public bool HasCapacityNow()
         {
+            // Returns true when this bus has a non-zero actual capacity at this point
+            //  in its route.
             return this.route.CurrentCapacity() > 0;
         }
     }

### 2019-04-22 Smart-Bus/Utilities/BusStop.cs

@@ -33,7 +33,7 @@ namespace Smart_Bus
         public Bus_info[] bus_list;
         public Request[] request_list;
         public int pending_request_index;
-        public const int urgencyThreshold = 300000; //5 minutes
+        public const int urgencyThreshold = int.MaxValue; // Requests are always "urgent"
         public DateTime SimStart;
         public int numBuses;
         public int num_route_info_rsp_rcvd;
@@ -98,8 +98,7 @@ namespace Smart_Bus
 
         public int Lookup_request()
         {
-            TimeSpan elapsedTime = DateTime.Now - SimStart;
-            int simulationMillis = (int)elapsedTime.Milliseconds;
+            int simulationMillis = Utilities.ElapsedSimulationMillis();
             int min_latestServingTime = 10000000;
             int served_request_index = -1;
 
@@ -137,7 +136,8 @@ namespace Smart_Bus
             {
                 //There is no urgent request, start a timer to assign requests later
                 stop_state = BusStop_State.REQUEST_WAIT_FOR_TIMER;
-                new Timer(new TimerCallback(request_lookup_timer_handler), null, request_list[served_request_index].destination.latestServingTime - (simulationMillis + urgencyThreshold), 0);
+                int timerDuration = (request_list[served_request_index].destination.latestServingTime - (simulationMillis + urgencyThreshold)) / Constants.TIME_MULTIPLIER;
+                new Timer(new TimerCallback(request_lookup_timer_handler), null, timerDuration, 0);
             }
 
             return -1;

### 2019-04-22 Smart-Bus/Utilities/Constants.cs

@@ -11,9 +11,9 @@ namespace Smart_Bus
 
         // 1 is Real Time (i.e., one second of wall time per second of simulation time)
         // Suggested values are on the order of 100 (every 10 milliseconds of wall time is one second of simulation time)
-        public static readonly int TIME_MULTIPLIER = 100;
+        public static readonly int TIME_MULTIPLIER = 60;
 
-        // DateTime format string for all messages
+        // DateTime format stuff for all messages
         public static string DATE_TIME_FORMAT = "yyyy'-'MM'-'dd'T'H':'mm':'ss.fff";
         public static char[] DATE_FORMAT_SEPARATORS = new char[] { '-', 'T', ':', '.' };
         public static int BUS_START_TIME;

### 2019-04-22 Smart-Bus/Utilities/IMessagePayload.cs

@@ -13,6 +13,9 @@ namespace Smart_Bus
         //  PayloadSimpleString
         //  PayloadRouteRequestForward
         //  PayloadRouteChangeAckResponse
+        // This interface provides a way to store (semi)arbitrary
+        //  data types in a message, and to standardize message
+        //  formats without specifying it explicitly.
 
         string BuildPayload();
     }

### 2019-04-22 Smart-Bus/Utilities/PayloadRouteChangeAckResponse.cs

@@ -3,6 +3,7 @@ using Microsoft.SPOT;
 
 namespace Smart_Bus
 {
+    // The payload class for ROUTE_CHANGE_ACK messages
     public class PayloadRouteChangeAckResponse: IMessagePayload
     {
         public bool didAcceptRouteChange;

### 2019-04-22 Smart-Bus/Utilities/PayloadRouteRequestForward.cs

@@ -3,6 +3,8 @@ using Microsoft.SPOT;
 
 namespace Smart_Bus
 {
+    // Not used. Payload class for ROUTE_REQUEST_FORWARD messages,
+    //  to be used in the future as part of the BFS operation.
     public class PayloadRouteRequestForward: IMessagePayload
     {
         int originalSource;

### 2019-04-22 Smart-Bus/Utilities/PayloadSimStart.cs

@@ -3,6 +3,7 @@ using Microsoft.SPOT;
 
 namespace Smart_Bus
 {
+    // Payload class for SIMULATION_START messages
     public class PayloadSimStart : IMessagePayload
     {
         public DateTime date;

### 2019-04-22 Smart-Bus/Utilities/PayloadSimpleString.cs

@@ -3,6 +3,7 @@ using Microsoft.SPOT;
 
 namespace Smart_Bus
 {
+    // Used primarily to mimic an "empty" payload.
     public class PayloadSimpleString: IMessagePayload
     {
 

### 2019-04-22 Smart-Bus/Utilities/Request.cs

@@ -5,8 +5,14 @@ using System.Text;
 
 namespace Smart_Bus
 {
+    // Payload class for PASSENGER_REQUEST messages
     public class Request : IComparable, IMessagePayload
     {
+        // A Request consists primarily of two Request_v's, origin and destination.
+        //  Additionally, a Request contains its requestId and the time at which the
+        //  passenger sent this request, as well as a boolean indicating whether
+        //  this request has been delayed.
+
         public int requestId;
         public int requestSendTime;
         public Request_v origin;
@@ -52,7 +58,9 @@ namespace Smart_Bus
         {
             // After the header, the array is organized as follows:
             //  [earliestPickupTime, latestDeliveryTime, origin, destination]
-            // where the times are in ms since simulation start
+            // where the times are in ms since simulation start.
+
+            // This method *changes the value of startIdx*!!
 
             int requestId = int.Parse(messageComponents[startIdx++]);
             int earliestPickupTime = int.Parse(messageComponents[startIdx++]);
@@ -101,6 +109,9 @@ namespace Smart_Bus
         }
     }
 
+    // Used as part of a payload made up of a Route; not used directly in Payloads.
+    // However this class is used extensively in BusStop and BusStopDriver. It
+    //  represents one "end" of a request. A sequence of Request_v makes up a Route.
     public class Request_v : IMessagePayload
     {
         public int requestId;

### 2019-04-22 Smart-Bus/Utilities/Route.cs

@@ -5,8 +5,13 @@ using System.Text;
 
 namespace Smart_Bus
 {
+    // Payload class for ROUTE_INFO_RESPONSE, ROUTE_CHANGE_REQUEST, and as
+    //  a component in PayloadRouteChangeAckResponse
     public class Route : IMessagePayload
     {
+        // A route consists of a sequence of "important stops", that is, those
+        //  at which we are eiter picking up or dropping off a passenger.
+
         IList importantStops;
 
         // NumServed marks served requests as such, in addition to
@@ -46,6 +51,10 @@ namespace Smart_Bus
         public Route()
         {
             this.importantStops = new ArrayList();
+
+            // These lines of code are commented out due to a (arbitrary) design decision
+            //  to exclude from a route the Terminus and Bus start/end times, opting instead
+            //  to keep these uniform for all buses and thus accessible from anywhere.
             //BusStop terminusStop = new BusStop(Bus.TERMINUS);
             //Request_v terminusStart = new Request_v(-1, Bus.START_TIME, Bus.END_TIME, true, terminusStop, false);
             //Request_v terminusEnd = new Request_v(-1, Bus.START_TIME, Bus.END_TIME, false, terminusStop, false);
@@ -64,6 +73,8 @@ namespace Smart_Bus
 
         public Route(string[] messageComponents, ref int startIdx)
         {
+            // This method *changes the value of startIdx*!!
+
             this.importantStops = new ArrayList();
             while (startIdx < messageComponents.Length)
             {
@@ -102,6 +113,8 @@ namespace Smart_Bus
             return removed;
         }
 
+        // Returns true if Route other serves at least the requests this route
+        //  is already serving.
         public bool IsRequestSubsetOf(Route other)
         {
             bool requestsMatch = true;
@@ -133,6 +146,7 @@ namespace Smart_Bus
             return payload.ToString();
         }
 
+        // Returns the capacity of this bus at the current time.
         internal int CurrentCapacity()
         {
             int elapsedSimulationMillis = Utilities.ElapsedSimulationMillis();

### 2019-04-22 Smart-Bus/Utilities/SBMessage.cs

@@ -11,6 +11,10 @@ namespace Smart_Bus
 {
     public class SBMessage
     {
+        // Used to standardize message formats without explicitly agreeing upon a particular one.
+
+        // Used for emulating directed messages in the all-broadcast network of the
+        //  Samraksh Emulator
         public struct MessageEndpoint
         {
             public enum EndpointType
@@ -42,6 +46,7 @@ namespace Smart_Bus
             }
         }
 
+        // The header of a message; includes the message type, originating node, and destination node
         public struct MessageHeader
         {
             public const int Length = 5;
@@ -101,9 +106,9 @@ namespace Smart_Bus
             this._payload = payload;
         }
 
+        // Parses a string into a message
         public SBMessage(string msgString)
         {
-            Debug.Print("Received Message: " + msgString);
             string[] components = msgString.TrimEnd().Split();
 
             int mTypeInt = int.Parse(components[0]);
@@ -154,11 +159,11 @@ namespace Smart_Bus
             return msg.ToString();
         }
 
+        // Broadcasts a message over NetPort, and prints a Debug statement.
         public void Broadcast(NetInst NetPort)
         {
             Debug.Print(DateTime.Now.ToString("HH:mm:ss.fff") + ": Sending message " + this.ToString());
             byte[] msgBytes = Utilities.StringToByteArray(this.ToString());
-            Thread.Sleep(100);
             NetPort.Broadcast(msgBytes, msgBytes.Length);
         }
     }

### 2019-04-22 Smart-Bus/Utilities/Utilities.cs

@@ -9,16 +9,23 @@ namespace Smart_Bus
     {
         public static DateTime SimStart;
 
+        // Returns the number of (real) milliseconds since the simulation began.
         public static int ElapsedMillis()
         {
             return (int)((DateTime.Now.Ticks - SimStart.Ticks) / TimeSpan.TicksPerMillisecond);
-            //TimeSpan elapsedTime = DateTime.Now - SimStart;
-            //return (int)elapsedTime.TotalMilliseconds;
         }
 
+        // Returns the number of (simulated) milliseconds since the simulation begain.
         public static int ElapsedSimulationMillis()
         {
             return ElapsedMillis() * Constants.TIME_MULTIPLIER;
+        }
+
+        // Returns the real-time equivalent of simulationMillis ms, given the
+        //  time multiplier in Constants.
+        public  static int GetRealTimeEquivalent(int simulationMillis)
+        {
+            return simulationMillis / Constants.TIME_MULTIPLIER;
         }
 
         public static void Main(String[] args)

### 2019-04-22 Smart-Bus/RequestPattern_2P_2S_1B.cs
Update RequestPattern_2P_2S_1B.cs

@@ -4,7 +4,7 @@ using Smart_Bus;
 
 namespace Smart_Bus
 {
-    // Request Pattern with 2 passenger, 2 stops, and 1 bus
+    // Request Pattern with 2 passengers, 2 stops, and 1 bus
     class RequestPattern_2P_2S_1B : IRequestPattern
     {
 

### 2019-04-22 Report/paper.tex
Update paper.tex

@@
 \section{Conclusion}
+In this project, we propose the smart bus system to offer a flexible usage for dynamically calculating the route to serve passengers and efficiently shorten the regular route to save more waiting time of passengers as well as travel time of buses.
+A low power Bus Service Access Points (BSAPs) with Wi-Fi and LPWAN interfaces operates as the mobile or static node to form a mobile ad-hoc network to provide high speed transmission in short distance and low speed transmission in long distance for connectivity.
+Due to its property of low power and portability, this network can be easily deployed to satisfy different topologies and provide pickup/delivery service even though within the area out of Internet coverage.
+All BSAPs composing a closed network can serve passengers over different locations in a distributed way.
+Thus, compared to traditional approach with centralized processing, the proposed distributed algorithm makes the network message complexity reduced and time complexity comparable.
+
+Adapting to the real time passenger requests, the dynamic route scheduling problem in the smart bus system is to minimize the total travel time, sum of lateness over all pick-up and delivery locations, and sum of overtime over all buses.
+This distributed algorithm focuses on solving the problem by introducing the concept of route flexibility of each bus.
+Therefore, maximizing the total route flexibility also achieve the optimization of the problem.
+Moreover, the route assignment scheme is proposed to consider the urgency of requests to effectively achieve the flexibility optimization.
+
+Our implementation aims to demonstrate the generation of request as passengers at different locations launch request at different time, the process of assigning requests from bus stops to the matched buses, and the route information updating for buses to sharing the current route and served passenger information to necessary bus stop.
+The Samraksh Emulator is feasible to implement the relevant features and easy to show all passenger, bus, and bus stop activities within a short time.
+The implementation is composed by three different kinds of nodes, request driver, bus driver, and bus stop driver, which simulate how passenger requests are served and how bus routes are optimized by maximizing the route flexibility in a smart bus system.
+
+The simulation results show that the bus scheduling algorithm acts with less bus travel time and less lateness over service locations compared to the scenario of the traditional fixed route buses.
+Also, the simulated system can resolve the problem of inconsistency.
+(For example, a request is served by more than one buses.) Last but not the least, we encounter some message errors when increasing the number of bus stops.
+The system might stop since one of the bus stops received an unexpected message from network.
+Otherwise, the functionalities of request driver, bus driver, and bus stop driver work well with different scenario combinations.
 

### 2019-04-22 Report/paper.tex
Revised and extended the results and evaluation section

@@
 % Sections
-\section{Assignment Description}
-Your final project report should include:
-\begin{itemize}
-	\item A write-up describing
-	\begin{itemize}
-		\item The design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API
-		\item Instructions and illustration of use, in terms of a README file and/or user guide,
-		\item How your implementation has been tested,
-		\item Performance of your implementation,
-		\item Assumptions or limitations of your design,
-		\item Any omissions or errors in your implementation, and
-		\item Any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)
-	\end{itemize}
-	\item Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.
-	\item Script of a session showing the program under test.
-\end{itemize}
+% \section{Assignment Description}
+% Your final project report should include:
+% \begin{itemize}
+% 	\item A write-up describing
+% 	\begin{itemize}
+% 		\item The design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API
+% 		\item Instructions and illustration of use, in terms of a README file and/or user guide,
+% 		\item How your implementation has been tested,
+% 		\item Performance of your implementation,
+% 		\item Assumptions or limitations of your design,
+% 		\item Any omissions or errors in your implementation, and
+% 		\item Any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)
+% 	\end{itemize}
+% 	\item Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.
+% 	\item Script of a session showing the program under test.
+% \end{itemize}
 
@@
 \subsubsection{Request Patterns}
-A variety of request patterns were used for evaluation. The scale of these patterns range from two passengers to ???, from two bus stops to ???, and from two buses to ???.
+A variety of request patterns were used for evaluation.
+The scale of these patterns range from two passengers to eight, from two bus stops to eight, and from one bus to four.
+The naming scheme depicts the number of passengers (\lstinline{P}), the number of bus stops (\lstinline{S}), and the number of buses it expects (\lstinline{B}).
+For example, a request pattern wihch produces requests for 6 passengers, in a network with 4 bus stops and 3 buses would have the name 6P\_4S\_3B.
+
+Table~\ref{tbl:smart-bus} summarizes the results for those Request Patterns in which the Emulator network bug did not manifest, or if it did, those patterns for which we could manually compute the lateness and minimum number of buses required.\footnote{Minimum No.
+of Buses is the smallest number of buses for which the lateness $\ell \leq 0$, or the number of buses which gives the lowest total lateness if it it not possible to serve all requests on time.}
+
+\setlength{\tabcolsep}{1em}
+\begin{table}[htbp]
+\centering
+\caption{Evaluating the Smart Bus Approach.}
+\begin{tabular}{c c c}
+Request Pattern & Total Lateness & Minimum No. of Buses \\ \hline
+1P\_2S\_1B & $-3$ & $1$ \\
+2P\_2S\_1B & $-7$ & $1$ \\
+2P\_4S\_1B & $2$  & $2$ \\
+\end{tabular}
+\label{tbl:smart-bus}
+\end{table}
 
@@
 By repeatedly applying these calculations, we compute the minimum number of buses required to serve all requests in time.
+The results are summarized in Table~\ref{tbl:traversal}.
 
@@
 \begin{tabular}{c c c}
-Request Pattern & Min \# of Buses & Total Lateness \\ \hline
-1P\_2S\_1B & $1$ & $-8$ \\
-2P\_2S\_1B & $1$ & $-1$ \\
-2P\_4S\_1B & $2$ & $5$ \\
-\hline
+Request Pattern & Total Lateness & Minimum No. of Buses \\ \hline
+1P\_2S\_1B & $-6$ & $1$ \\
+2P\_2S\_1B & $-1$ & $1$ \\
+2P\_4S\_1B & $5$  & $2$ \\
 \end{tabular}
@@
 Considerations made include accounting for the fact that, in the real world, passengers will be aware of the schedule and will appear at stops approximately when a bus would be there.
-However, the results to point to the fact that the Smart Bus algorithm improves on the traversal approach for these patterns.
+However, the results point to the fact that the Smart Bus algorithm improves on the traversal approach for these patterns.
 
 \section{Using the Smart-Bus Application}
-There are several steps to running the application:
+There are several steps to running the application, which must be done in order:
 \begin{itemize}
-	\item Launch $n$ instances of \lstinline{Bus-Driver}
-	\item Launch $m$ instances of \lstinline{Bus-Stop-Driver}
+  \item Launch a \emph{fresh} instance of the Samraksh Emulator NetworkHub
+	\item Launch $n$ instances of \lstinline{Bus-Stop-Driver}
+	\item Launch $m$ instances of \lstinline{Bus-Driver}
 	\item Ensure the simulation parameters of \lstinline{Request-Driver} match the number of buses and stops that have been launched
-	\item Launch an instance of \lstinline{Request-Driver} with the requisite simulation parameters (i.e., Request Pattern and Time Multiplier)
+	\item Launch a single instance of \lstinline{Request-Driver} with the requisite simulation parameters (i.e., Request Pattern and Time Multiplier)
 	\item Wait for simulation to conclude
 \end{itemize}
+
+The order of these steps is imperative because the Request Driver relies on predictable Bus Stop IDs, which are assigned based on the \lstinline{appId} given to the node from the network.
+Specifically, the Request Driver expects that Bus Stop nodes have consecutive IDs in $[1, n]$.
 
@@
 
-\newpage
-\appendix
-\section{Source Code}
-
 % \bibliographystyle{abbrv}

### 2019-04-22 Smart-Bus/Utilities/BusStop.cs
Update BusStop.cs

@@ -8,22 +8,32 @@ namespace Smart_Bus
     public struct Bus_info
     {
         public int busId;
-        public const int capacity = 5;
-        public int terminusLocation;
+        public const int capacity = 5; //the maximal seats for passenger
+        public int terminusLocation; //the id of bus terminus
         public int busStartTime; //ts_k: expected start time at terminus 
         public int busEndTime; //te_k: expected end time terminus
-        public int NumServed;
-        public Request_v[] routeInfo;
-        public Request_v[] pending_routeInfo;
+        public int NumServed; //the number of served location in the route
+        public Request_v[] routeInfo; //the current route info
+        public Request_v[] pending_routeInfo; //the temprorary route info when adding a new request to current route
     }
 
     public enum BusStop_State
     {
         REQUEST_NULL = 0,
+        /* There is no request in request_list to assign */
+
         REQUEST_WAIT_FOR_ROUTE_INFO = 1,
+        /* Whenever BusStop send ROUTE_INFO_REQUEST to all buses, */
+        /* BusStop should wait all ROUTE_INFO_RESPONSE message to synchronize the newest route info of all buses */
+
         REQUEST_READY_TO_BE_ASSIGNED = 2,
+        /* There is no pending request assignment, BusStop can start to assign a urgent request from request_list */
+
         REQUEST_WAIT_FOR_TIMER = 3,
+        /* There is no pending request assignment and no urgent requests, BusStop starts a timer to wait to assign the closest urgent request */
+
         REQUEST_ASSIGNED_AND_SENDING_TO_BUS = 4
+        /* There is a pending request sent to matched bus, BusStop need to wait for ROUTE_CHANGE_ACK */
     }
     
     public class BusStop
@@ -32,11 +42,11 @@ namespace Smart_Bus
         public BusStop_State stop_state;
         public Bus_info[] bus_list;
         public Request[] request_list;
-        public int pending_request_index;
+        public int pending_request_index; //the index of pending request in request_list
         public const int urgencyThreshold = int.MaxValue; // Requests are always "urgent"
         public DateTime SimStart;
-        public int numBuses;
-        public int num_route_info_rsp_rcvd;
+        public int numBuses;  //number of buses in the system
+        public int num_route_info_rsp_rcvd; //number of ROUTE_INFO_RESPONSE received so far
 
         public BusStop(int id)
         {
@@ -49,16 +59,13 @@ namespace Smart_Bus
 
[…]

### 2019-04-22 Bus-Stop/BusStopDriver.cs
Update BusStopDriver.cs

@@ -89,7 +89,7 @@ namespace Smart_Bus
                         }
                     case SBMessage.MessageType.SEND_PASSENGER_REQUEST:
                         {
-                            //Send ROUTE_INFO_REQUEST to buses while receiving a request but the stop does not have route info
+                            //Always send ROUTE_INFO_REQUEST to buses while receiving a request
                             SBMessage.MessageEndpoint origin = new SBMessage.MessageEndpoint(SBMessage.MessageEndpoint.EndpointType.BUS_STOP, instance.myBusStop.id);
                             SBMessage.MessageEndpoint destination = new SBMessage.MessageEndpoint();
                             SBMessage m = new SBMessage(SBMessage.MessageType.ROUTE_INFO_REQUEST, origin, destination, new PayloadSimpleString());
@@ -99,6 +99,8 @@ namespace Smart_Bus
                             {
                                 case BusStop_State.REQUEST_NULL:
                                 case BusStop_State.REQUEST_READY_TO_BE_ASSIGNED:
+
+                                    //BusStop has to wait for receving all ROUTE_INFO_RESPONSE, then it's allowed to assigned requests
                                     instance.myBusStop.stop_state = BusStop_State.REQUEST_WAIT_FOR_ROUTE_INFO;
 
                                     //reset the counter for collecting ROUTE_INFO_RESPONSE
@@ -139,20 +141,25 @@ namespace Smart_Bus
                             element.busEndTime = Bus.END_TIME;
                             element.terminusLocation = Bus.TERMINUS;
 
+                            //Save the bus info and route info to bus_list
                             instance.myBusStop.Update_busRoute(element);
 
                             switch (instance.myBusStop.stop_state)
                             {
                                 case BusStop_State.REQUEST_WAIT_FOR_ROUTE_INFO:
+                                    //Increase the num of recevied ROUTE_INFO_RESPONSE
                                     instance.myBusStop.num_route_info_rsp_rcvd++;
 
                                     if (instance.myBusStop.num_route_info_rsp_rcvd == instance.myBusStop.numBuses)
                                     {
+                                        //received all ROUTE_INFO_RESPONSE, then BusStop have enough route info to assign request
                                         instance.myBusStop.stop_state = BusStop_State.REQUEST_READY_TO_BE_ASSIGNED;
+                                        
                                         //Start to assign request
                                         int bus_index = instance.myBusStop.Lookup_request();
                                         if (bus_index != -1)
                                         {
[…]

### 2019-04-22 Report/paper.tex
Final touches on the report

@@
 \usepackage{pdflscape}
+
+\usepackage{hyperref}
 
@@
 % Sections
-% \section{Assignment Description}
-% Your final project report should include:
-% \begin{itemize}
-% 	\item A write-up describing
-% 	\begin{itemize}
-% 		\item The design rationale of the module(s) you developed, along with the algorithm you have designed/used and a detailed API
-% 		\item Instructions and illustration of use, in terms of a README file and/or user guide,
-% 		\item How your implementation has been tested,
-% 		\item Performance of your implementation,
-% 		\item Assumptions or limitations of your design,
-% 		\item Any omissions or errors in your implementation, and
-% 		\item Any bugs or weaknesses you have found in the algorithm/protocol. (Only if some of these do not apply to your project should you omit them.)
-% 	\end{itemize}
-% 	\item Program sources and executable (including any test programs). Credit will be reserved for the quality of documentation of your programs.
-% 	\item Script of a session showing the program under test.
-% \end{itemize}
-
 \section{Introduction}
@@
 The simulation results show that the bus scheduling algorithm acts with less bus travel time and less lateness over service locations compared to the scenario of the traditional fixed route buses.
-Also, the simulated system can resolve the problem of inconsistency.
+Also, the simulated system can resolve the problem of redundancy.
 (For example, a request is served by more than one buses.) Last but not the least, we encounter some message errors when increasing the number of bus stops.
@@
 
-% \bibliographystyle{abbrv}
-% \bibliography{merged-bibliography,siv-bibliography,bibliography_3,bibliography_lastminute,Xiong2017Abstract} % ,weide-bibliography}
+\newpage
+\appendix
+\section{Source Code}
+The source code (including the \LaTeX\ source for this report) is available at \url{https://github.com/alanweide/Smart-Bus.git}.
+If there is any trouble accessing the Git repository, please contact Alan Weide (\href{mailto:weide.3@osu.edu}{weide.3@osu.edu}).
+
+This project was implemented in C\# using the \href{https://marketplace.visualstudio.com/items?itemName=SteveMaillet.NETMicroFrameworkSDK43QFE2}{.NET Microframework 4.3 (QEF2)}.
+The easiest way to navigate the project is to use \href{https://visualstudio.microsoft.com/vs/older-downloads/}{Visual Studio 2013}.
+To run the program, you must have the \href{https://www.dropbox.com/sh/dtcgec1pe3mpkim/AAC318cuhoLaw4AtoL7dYDmYa?dl=0}{Samraksh Emulator} installed and registered.
 
